---
title: "SEACAR Oyster Analysis"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    toc: TRUE
    toc_depth: 2
  html_document:
    toc: TRUE
    toc_float: TRUE
    toc_depth: 2
    dev: png
    keep_md: yes
  pdf_document:
    toc: TRUE
    toc_depth: 2
    dev: png
    extra_dependencies: ["float"]
    keep_md: yes
urlcolor: blue
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{makecell}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{array}
  \usepackage{multirow}
  \usepackage{wrapfig}
  \usepackage{colortbl}
  \usepackage{pdflscape}
  \usepackage{tabu}
  \usepackage{threeparttable}
  \usepackage{threeparttablex}
  \usepackage[normalem]{ulem}
  \usepackage[utf8]{inputenc}
  \usepackage{makecell}
  \usepackage{xcolor}
  \usepackage{graphicx}
  \floatplacement{figure}{H}
---

# Important Notes

The purpose of this script is to group oyster data, create managed area statistics, perform lme analysis on density, percent live, and shell height, and create reports in pdf and Word document form for Oyster data.

All scripts and outputs can be found on the SEACAR GitHub repository:

https://github.com/FloridaSEACAR/SEACAR_Trend_Analyses

This markdown file is designed to be compiled by [Oyster_ReportRender.R](https://github.com/FloridaSEACAR/SEACAR_Trend_Analyses/blob/main/Oyster/Oyster_ReportRender.R) (https://github.com/FloridaSEACAR/SEACAR_Trend_Analyses/blob/main/Oyster/Oyster_ReportRender.R).

This script is based off of code originally written by Stephen Durham.

Compiled and edited by [J.E. Panzik](jepanzik@usf.edu) and [Tyler Hill](Tyler.Hill@FloridaDEP.gov) for SEACAR.

# Libraries and Settings

Loads libraries used in the script. Loads the Segoe UI font for use in the figures. The inclusion of `scipen` option limits how frequently R defaults to scientific notation. Sets default settings for displaying warning and messages in created document, and sets figure dpi.

```{r Libraries, message=FALSE}
library(lubridate)
library(tidyverse)
library(data.table)
library(tictoc)
library(glue)
library(kableExtra)
options(scipen=999)
knitr::opts_chunk$set(
   warning=FALSE,
   message=FALSE,
   dpi=200,
   fig.pos = 'H'
)
options(kableExtra.auto_format = FALSE)
options(knitr.kable.NA = '-')
```



# File Import

Imports file that is determined in the Oyster_ReportRender.R script. 

The command `fread` is used because of its improved speed while handling large data files. Updates column names.

The latest version of Oyster data is available at: https://usf.box.com/s/6dtcrcdkrtc33fqw5kl5fjo6guo0anrw

The file being used for the analysis is: **`r file_short`**

```{r FileImport, eval=F, echo=T}
oysterraw <- fread(file_in, sep="|", na.strings=c("NULL"))
oysterraw2 <- pivot_wider(oysterraw, names_from="ParameterName",
                          values_from="ResultValue")
setDT(oysterraw2)
setnames(oysterraw2, c("Density", "Percent Live", "Shell Height",
                       "Number of Oysters Counted - Live",
                       "Number of Oysters Counted - Dead",
                       "Number of Oysters Counted - Total", "Reef Height"),
         c("Density_m2", "PercentLive_pct", "ShellHeight_mm",
           "Number_of_Oysters_Counted_Live_Count",
           "Number_of_Oysters_Counted_Dead_Count",
           "Number_of_Oysters_Counted_Total_Count",
           "ReefHeight_mm"))
oysterraw2[, ObsIndex := seq(1:nrow(oysterraw2))]

oysterraw <- oysterraw2
rm(oysterraw2)
```



# Generate Universal Reef IDs

Individual IDs are given to reefs based on location within GIS files. This process now occurs separately from the Oyster habitat scripts and the UniversalReefID will be maintained within the database.

```{r ReefID, eval=F, echo=T}
# Output from oyster ID script (will make autonomous)
new_crosswalk2 <- readRDS("data/new_crosswalk2.rds")

oysterraw2 <- merge(oysterraw[, -c("UniversalReefID")], 
                    new_crosswalk2 %>% 
                      select(c("UniversalReefID", "LocationID")), 
                    by = "LocationID")
oysterraw <- oysterraw2
rm(oysterraw2)
```


# Data Setup & Filtering

Documentation on database filtering is provided here: [SEACAR Documentation- Analysis Filters and Calculations.docx](https://github.com/FloridaSEACAR/SEACAR_Panzik/blob/main/SEACAR%20Documentation%20-%20Analysis%20Filters%20and%20Calculations.docx)

Identifies and removes outliers in the data and various programs.

```{r DataSetup, eval=F, echo=T}
#Make sure column formats are correct-I am still getting an "NAs introduced
#by coercion" warning on the LiveDate calculation, 
#but I'm not sure what is going on because when I spot-check the output,
#it does not look like it is introducing NAs...
oysterraw[, `:=` (RowID=as.integer(RowID),
                  ProgramID=as.integer(ProgramID),
                  LocationID=as.integer(LocationID),
                  ProgramName=as.character(ProgramName),
                  ProgramLocationID=as.character(ProgramLocationID),
                  QuadIdentifier=as.character(QuadIdentifier),
                  ReefIdentifier=as.character(ReefIdentifier),
                  UniversalReefID=as.factor(UniversalReefID),
                  LiveDate=as.integer(ifelse(!is.na(LiveDate_Qualifier) &
                                               str_detect(LiveDate,
                                                          "....-..-.."), 
                                             paste0(str_sub(LiveDate, 1, 4)), 
                                             round(as.numeric(LiveDate)))),
                  LiveDate_Qualifier=as.character(LiveDate_Qualifier),
                  LiveDate_MinEstDate=as.numeric(LiveDate_MinEstDate),
                  LiveDate_MaxEstDate=as.numeric(LiveDate_MaxEstDate),
                  SampleAge_Stdev=as.numeric(SampleAge_Stdev),
                  #GISUniqueID=as.logical(GISUniqueID),
                  Year=as.integer(Year),
                  Month=as.integer(Month),
                  ManagedAreaName=as.character(ManagedAreaName),
                  SurveyMethod=as.character(SurveyMethod),
                  PercentLiveMethod=as.character(PercentLiveMethod),
                  HabitatClassification=as.character(HabitatClassification),
                  MinimumSizeMeasured_mm=as.character(MinimumSizeMeasured_mm),
                  NumberMeasured_n=as.character(NumberMeasured_n),
                  QuadSize_m2=as.numeric(QuadSize_m2),
                  MADup=as.integer(MADup),
                  Density_m2=as.numeric(Density_m2),
                  PercentLive_pct=as.numeric(PercentLive_pct),
                  ShellHeight_mm=as.numeric(ShellHeight_mm),
                  Number_of_Oysters_Counted_Total_Count =
                    as.integer(Number_of_Oysters_Counted_Total_Count),
                  Number_of_Oysters_Counted_Live_Count =
                    as.integer(Number_of_Oysters_Counted_Live_Count),
                  Number_of_Oysters_Counted_Dead_Count =
                    as.integer(Number_of_Oysters_Counted_Dead_Count),
                  ObsIndex=as.integer(ObsIndex))]

#Calculate Density_m2 values for ProgramID==4016 & 4042
oysterraw[ProgramID==4016, Density_m2 :=
            Number_of_Oysters_Counted_Live_Count/as.numeric(QuadSize_m2)]
oysterraw[ProgramID==4042 & !is.na(Number_of_Oysters_Counted_Live_Count),
          Density_m2 :=
            Number_of_Oysters_Counted_Live_Count/as.numeric(QuadSize_m2)]

#Remove "25" values from total counts column, make all "PercentLiveMethod"
#values the same, and calculate estimated live Density for ProgramID==5074 and 
oysterraw <- oysterraw[RowID %in%
                         setdiff(
                           oysterraw[, RowID],
                           oysterraw[ProgramID ==5074 &
                                       Number_of_Oysters_Counted_Total_Count==25, RowID]), ]
oysterraw[ProgramID==5074, PercentLiveMethod := "Estimated percent"]
oysterraw[ProgramID==5074, SampleDate :=
            unique(oysterraw[ProgramID==5074 &
                               !is.na(Number_of_Oysters_Counted_Total_Count),
                             SampleDate])[1]]

#Some PercentLiveMethod values for ID4042 are NA
oysterraw[ProgramID==4042 | ProgramID==4016,
          PercentLiveMethod := "Point-intercept"]

#make sure quadrat identifiers are unique
oysterraw[, QuadIdentifier_old := QuadIdentifier]
oysterraw[, QuadIdentifier := paste(UniversalReefID,
                                    LocationID, Year, Month,
                                    QuadIdentifier_old, sep="_")]

oysterraw[, MA_plotlab := paste0(ManagedAreaName, "_", HabitatClassification)]
subtidal <- c(4044, 5007, 5071, 5073)
oysterraw[, Subtidal := ifelse(ProgramID %in% subtidal, 1, 0)][, Subtidal := as.logical(Subtidal)]

#Create variables for relative year and size class category for data that
#should be included in analyses and counts of live oysters measured
for(i in unique(oysterraw$ManagedAreaName)){
  oysterraw[ManagedAreaName==i & !is.na(LiveDate), `:=`
            (RelYear=(LiveDate-min(LiveDate))+1,
              YearDiff=min(LiveDate)-1,
              #adding 1 to each RelYear to avoid min(RelYear)==0,
              #because it is used later as an index for plotting years so
              #it needs to start from 1
              SizeClass=fcase(ShellHeight_mm >= 25 &
                                ShellHeight_mm < 75, "25to75mm",
                              ShellHeight_mm >= 75, "o75mm",
                              default=NA))]
  
  oysterraw[ManagedAreaName==i & !is.na(LiveDate),
            counts := length(ShellHeight_mm), by=c("QuadIdentifier")]
}

#Remove unrealistically high shell heights from ID_5017
oysterraw <- setdiff(oysterraw, oysterraw[ProgramID==5017 & ShellHeight_mm >= 165, ])

#Create data table to save model results
oysterresults <- data.table(indicator=character(),
                            managed_area=character(),
                            habitat_class=character(),
                            size_class=character(),
                            live_date_qual=character(),
                            n_programs=integer(),
                            programs=list(),
                            filename=character(),
                            effect=character(),
                            component=character(),
                            group=character(),
                            term=character(),
                            estimate=numeric(),
                            std.error=numeric(),
                            conf.low=numeric(),
                            conf.high=numeric())

#How many years of data for each managed area/habitat class/indicator combination?  
setDT(oysterraw)
oysterraw[!is.na(Density_m2), `:=` (nyrpar="Density_m2",
                                    nyears=length(unique(Year))),
          by=MA_plotlab]
oysterraw[!is.na(PercentLive_pct), `:=` (nyrpar="PercentLive_pct",
                                         nyears=length(unique(Year))),
          by=MA_plotlab]
oysterraw[!is.na(ShellHeight_mm), `:=` (nyrpar="ShellHeight_mm",
                                        nyears=length(unique(Year))),
          by=MA_plotlab]
MAinclude <- distinct(oysterraw[, .(MA_plotlab, nyrpar, nyears)])
# View(MAinclude[!is.na(nyrpar) & nyears >= 5, ])

oysterraw[str_detect(MA_plotlab, "Pine Island Sound"),
           `:=` (MA_plotlab=ifelse(str_detect(ProgramLocationID,
                                              "Reference") |
                                     str_detect(ProgramLocationID,
                                                "Control"),
                                   "Pine Island Sound Aquatic Preserve_Natural",
                                   "Pine Island Sound Aquatic Preserve_Restored"),
                 HabitatClassification=ifelse(str_detect(ProgramLocationID,
                                                         "Reference") |
                                                str_detect(ProgramLocationID,
                                                           "Control"),
                                              "Natural", "Restored"))]

```



# Managed Area Statistics

Gets summary statistics for each managed area. Uses piping from dplyr package to feed into subsequent steps. Sets of summary statistics are performed for Density, Shell Height, and Percent Living. The following steps are performed:

1. Group data that have the same `ManagedAreaName`, `Year`, `Month`, `nyrpar`, `LiveDate_Qualifier`, `SizeClass`, and `HabitatClassification`.
   + Second summary statistics do not use the `Month` grouping and are only for `ManagedAreaName`, `Year`, and the other oyster parameters.
   + Third summary statistics do not use `Year` grouping and are only for `ManagedAreaName`, `Month`, and the other oyster parameters.
   + Fourth summary statistics are only grouped based on `ManagedAreaName` and the other oyster parameters
      + Determines the years that the minimum and maximum species richness occurred

2. For each group, provide the following information: Parameter Name (ParameterName), Number of Entries (N_Data), Lowest Value (Min), Largest Value (Max), Median, Mean, Standard Deviation, and a list of all Programs included in these measurements.
3. Sort the data in ascending (A to Z and 0 to 9) order based on `ManagedAreaName` then `Year` then `Month`
4. Write summary stats to a pipe-delimited .txt file in the output directory
   + [Oyster Output Files in SEACAR GitHub](https://github.com/FloridaSEACAR/SEACAR_Trend_Analyses/tree/main/Oyster/output) (https://github.com/FloridaSEACAR/SEACAR_Trend_Analyses/tree/main/Oyster/output)

##Density

```{r ma_stats_den, message=FALSE, eval=F, echo=T}
oysterraw$SizeClass[oysterraw$SizeClass=="25to75mm"] <- "25-75mm"
oysterraw$SizeClass[oysterraw$SizeClass=="35to75mm"] <- "35-75mm"
oysterraw$SizeClass[oysterraw$SizeClass=="o75mm"] <- ">75mm"

# Create summary statistics for each managed area based on Year and Month
# intervals.
MA_YM_Stats <- oysterraw[oysterraw$nyrpar=="Density_m2",] %>%
   group_by(AreaID, ManagedAreaName, Year, Month, nyrpar,
            LiveDate_Qualifier, SizeClass, HabitatClassification) %>%
   dplyr::summarize(N_Data=length(Density_m2[!is.na(Density_m2)]),
             Min=min(Density_m2[!is.na(Density_m2)]),
             Max=max(Density_m2[!is.na(Density_m2)]),
             Median=median(Density_m2[!is.na(Density_m2)]),
             Mean=mean(Density_m2[!is.na(Density_m2)]),
             StandardDeviation=sd(Density_m2[!is.na(Density_m2)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_YM_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_YM_Stats$ShellType[MA_YM_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_YM_Stats$ShellType[MA_YM_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName, Year, then Month
MA_YM_Stats <- as.data.table(MA_YM_Stats[order(MA_YM_Stats$ManagedAreaName,
                                               MA_YM_Stats$Year,
                                               MA_YM_Stats$Month,
                                               MA_YM_Stats$ShellType,
                                               MA_YM_Stats$SizeClass,
                                               MA_YM_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_YM_Stats, paste0(out_dir,"/Density/Oyster_Dens_MA_MMYY_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_YM_Stats)

# Create summary statistics for each managed area based on Year intervals
MA_Y_Stats <- oysterraw[oysterraw$nyrpar=="Density_m2",] %>%
   group_by(AreaID, ManagedAreaName, Year, nyrpar, LiveDate_Qualifier,
            SizeClass, HabitatClassification) %>%
   dplyr::summarize(N_Data=length(Density_m2[!is.na(Density_m2)]),
             Min=min(Density_m2[!is.na(Density_m2)]),
             Max=max(Density_m2[!is.na(Density_m2)]),
             Median=median(Density_m2[!is.na(Density_m2)]),
             Mean=mean(Density_m2[!is.na(Density_m2)]),
             StandardDeviation=sd(Density_m2[!is.na(Density_m2)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_Y_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_Y_Stats$ShellType[MA_Y_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_Y_Stats$ShellType[MA_Y_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName then Year
MA_Y_Stats <- as.data.table(MA_Y_Stats[order(MA_Y_Stats$ManagedAreaName,
                                             MA_Y_Stats$Year,
                                             MA_Y_Stats$ShellType,
                                             MA_Y_Stats$SizeClass,
                                             MA_Y_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_Y_Stats, paste0(out_dir,"/Density/Oyster_Dens_MA_Yr_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_Y_Stats)

# Create summary statistics for each managed area based on Month intervals.
MA_M_Stats <- oysterraw[oysterraw$nyrpar=="Density_m2",] %>%
   group_by(AreaID, ManagedAreaName, Month, nyrpar,
            LiveDate_Qualifier, SizeClass,
            HabitatClassification) %>%
   dplyr::summarize(N_Data=length(Density_m2[!is.na(Density_m2)]),
             Min=min(Density_m2[!is.na(Density_m2)]),
             Max=max(Density_m2[!is.na(Density_m2)]),
             Median=median(Density_m2[!is.na(Density_m2)]),
             Mean=mean(Density_m2[!is.na(Density_m2)]),
             StandardDeviation=sd(Density_m2[!is.na(Density_m2)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_M_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_M_Stats$ShellType[MA_M_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_M_Stats$ShellType[MA_M_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName then Month
MA_M_Stats <- as.data.table(MA_M_Stats[order(MA_M_Stats$ManagedAreaName,
                                             MA_M_Stats$Month,
                                             MA_M_Stats$ShellType,
                                             MA_M_Stats$SizeClass,
                                             MA_M_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_M_Stats, paste0(out_dir,"/Density/Oyster_Dens_MA_Mo_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_M_Stats)

# Create summary overall statistics for each managed area.
MA_Ov_Stats <- oysterraw[oysterraw$nyrpar=="Density_m2",] %>%
   group_by(AreaID, ManagedAreaName, nyrpar,
            LiveDate_Qualifier, SizeClass,
            HabitatClassification) %>%
   dplyr::summarize(N_Years=length(unique(
     LiveDate[!is.na(LiveDate) & !is.na(Density_m2)])),
             SufficientData=ifelse(N_Years>=5, TRUE, FALSE),
             EarliestLiveDate=min(LiveDate[!is.na(Density_m2)]),
             LatestLiveDate=max(LiveDate[!is.na(Density_m2)]),
             LastSampleDate=max(SampleDate),
             N_Data=length(Density_m2[!is.na(Density_m2)]),
             Min=min(Density_m2[!is.na(Density_m2)]),
             Max=max(Density_m2[!is.na(Density_m2)]),
             Median=median(Density_m2[!is.na(Density_m2)]),
             Mean=mean(Density_m2[!is.na(Density_m2)]),
             StandardDeviation=sd(Density_m2[!is.na(Density_m2)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_Ov_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_Ov_Stats$ShellType[MA_Ov_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_Ov_Stats$ShellType[MA_Ov_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName
MA_Ov_Stats <- as.data.table(MA_Ov_Stats[order(MA_Ov_Stats$ManagedAreaName,
                                               MA_Ov_Stats$ShellType,
                                               MA_Ov_Stats$SizeClass,
                                               MA_Ov_Stats$HabitatType), ])

# Replaces blank ProgramIDs with NA (missing values)
MA_Ov_Stats$ProgramIDs <- replace(MA_Ov_Stats$ProgramIDs,
                                  MA_Ov_Stats$ProgramIDs=="", NA)
MA_Ov_Stats$Programs <- replace(MA_Ov_Stats$Programs,
                                  MA_Ov_Stats$Programs=="", NA)
# Write overall statistics to file
fwrite(MA_Ov_Stats, paste0(out_dir,"/Density/Oyster_Dens_MA_Overall_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_Ov_Stats)
```

##Shell Height

```{r ma_stats_sh, message=FALSE, eval=F, echo=T}
# Create summary statistics for each managed area based on Year and Month
# intervals.
MA_YM_Stats <- oysterraw[oysterraw$nyrpar=="ShellHeight_mm",] %>%
   group_by(AreaID, ManagedAreaName, Year, Month, nyrpar,
            LiveDate_Qualifier, SizeClass, HabitatClassification) %>%
   dplyr::summarize(N_Data=length(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Min=min(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Max=max(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Median=median(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Mean=mean(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             StandardDeviation=sd(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_YM_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_YM_Stats$ShellType[MA_YM_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_YM_Stats$ShellType[MA_YM_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName, Year, then Month
MA_YM_Stats <- as.data.table(MA_YM_Stats[order(MA_YM_Stats$ManagedAreaName,
                                               MA_YM_Stats$Year,
                                               MA_YM_Stats$Month,
                                               MA_YM_Stats$ShellType,
                                               MA_YM_Stats$SizeClass,
                                               MA_YM_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_YM_Stats, paste0(out_dir,"/Shell_Height/Oyster_SH_MA_MMYY_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_YM_Stats)

# Create summary statistics for each managed area based on Year intervals
MA_Y_Stats <- oysterraw[oysterraw$nyrpar=="ShellHeight_mm",] %>%
   group_by(AreaID, ManagedAreaName, Year, nyrpar, LiveDate_Qualifier,
            SizeClass, HabitatClassification) %>%
   dplyr::summarize(N_Data=length(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Min=min(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Max=max(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Median=median(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Mean=mean(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             StandardDeviation=sd(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_Y_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_Y_Stats$ShellType[MA_Y_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_Y_Stats$ShellType[MA_Y_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName then Year
MA_Y_Stats <- as.data.table(MA_Y_Stats[order(MA_Y_Stats$ManagedAreaName,
                                             MA_Y_Stats$Year,
                                             MA_Y_Stats$ShellType,
                                             MA_Y_Stats$SizeClass,
                                             MA_Y_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_Y_Stats, paste0(out_dir,"/Shell_Height/Oyster_SH_MA_Yr_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_Y_Stats)

# Create summary statistics for each managed area based on Month intervals.
MA_M_Stats <- oysterraw[oysterraw$nyrpar=="ShellHeight_mm",] %>%
   group_by(AreaID, ManagedAreaName, Month, nyrpar,
            LiveDate_Qualifier, SizeClass,
            HabitatClassification) %>%
   dplyr::summarize(N_Data=length(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Min=min(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Max=max(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Median=median(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Mean=mean(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             StandardDeviation=sd(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_M_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_M_Stats$ShellType[MA_M_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_M_Stats$ShellType[MA_M_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName then Month
MA_M_Stats <- as.data.table(MA_M_Stats[order(MA_M_Stats$ManagedAreaName,
                                             MA_M_Stats$Month,
                                             MA_M_Stats$ShellType,
                                             MA_M_Stats$SizeClass,
                                             MA_M_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_M_Stats, paste0(out_dir,"/Shell_Height/Oyster_SH_MA_Mo_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_M_Stats)

# Create summary overall statistics for each managed area.
MA_Ov_Stats <- oysterraw[oysterraw$nyrpar=="ShellHeight_mm",] %>%
   group_by(AreaID, ManagedAreaName, nyrpar,
            LiveDate_Qualifier, SizeClass,
            HabitatClassification) %>%
   dplyr::summarize(N_Years=length(unique(
     LiveDate[!is.na(LiveDate) & !is.na(ShellHeight_mm)])),
             SufficientData=ifelse(N_Years>=5, TRUE, FALSE),
             EarliestLiveDate=min(LiveDate[!is.na(ShellHeight_mm)]),
             LatestLiveDate=max(LiveDate[!is.na(ShellHeight_mm)]),
             LastSampleDate=max(SampleDate),
             N_Data=length(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Min=min(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Max=max(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Median=median(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Mean=mean(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             StandardDeviation=sd(ShellHeight_mm[!is.na(ShellHeight_mm)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_Ov_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_Ov_Stats$ShellType[MA_Ov_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_Ov_Stats$ShellType[MA_Ov_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName
MA_Ov_Stats <- as.data.table(MA_Ov_Stats[order(MA_Ov_Stats$ManagedAreaName,
                                               MA_Ov_Stats$ShellType,
                                               MA_Ov_Stats$SizeClass,
                                               MA_Ov_Stats$HabitatType), ])

# Replaces blank ProgramIDs with NA (missing values)
MA_Ov_Stats$ProgramIDs <- replace(MA_Ov_Stats$ProgramIDs,
                                  MA_Ov_Stats$ProgramIDs=="", NA)
MA_Ov_Stats$Programs <- replace(MA_Ov_Stats$Programs,
                                  MA_Ov_Stats$Programs=="", NA)
# Write overall statistics to file
fwrite(MA_Ov_Stats, paste0(out_dir,"/Shell_Height/Oyster_SH_MA_Overall_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_Ov_Stats)
```

##Percent Live

```{r ma_stats_pct, message=FALSE, eval=F, echo=T}
# Create summary statistics for each managed area based on Year and Month
# intervals.
MA_YM_Stats <- oysterraw[oysterraw$nyrpar=="PercentLive_pct",] %>%
   group_by(AreaID, ManagedAreaName, Year, Month, nyrpar,
            LiveDate_Qualifier, SizeClass, HabitatClassification) %>%
   dplyr::summarize(N_Data=length(PercentLive_pct[!is.na(PercentLive_pct)]),
             Min=min(PercentLive_pct[!is.na(PercentLive_pct)]),
             Max=max(PercentLive_pct[!is.na(PercentLive_pct)]),
             Median=median(PercentLive_pct[!is.na(PercentLive_pct)]),
             Mean=mean(PercentLive_pct[!is.na(PercentLive_pct)]),
             StandardDeviation=sd(PercentLive_pct[!is.na(PercentLive_pct)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_YM_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_YM_Stats$ShellType[MA_YM_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_YM_Stats$ShellType[MA_YM_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName, Year, then Month
MA_YM_Stats <- as.data.table(MA_YM_Stats[order(MA_YM_Stats$ManagedAreaName,
                                               MA_YM_Stats$Year,
                                               MA_YM_Stats$Month,
                                               MA_YM_Stats$ShellType,
                                               MA_YM_Stats$SizeClass,
                                               MA_YM_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_YM_Stats, paste0(out_dir,"/Percent_Live/Oyster_PrcLive_MA_MMYY_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_YM_Stats)

# Create summary statistics for each managed area based on Year intervals
MA_Y_Stats <- oysterraw[oysterraw$nyrpar=="PercentLive_pct",] %>%
   group_by(AreaID, ManagedAreaName, Year, nyrpar, LiveDate_Qualifier,
            SizeClass, HabitatClassification) %>%
   dplyr::summarize(N_Data=length(PercentLive_pct[!is.na(PercentLive_pct)]),
             Min=min(PercentLive_pct[!is.na(PercentLive_pct)]),
             Max=max(PercentLive_pct[!is.na(PercentLive_pct)]),
             Median=median(PercentLive_pct[!is.na(PercentLive_pct)]),
             Mean=mean(PercentLive_pct[!is.na(PercentLive_pct)]),
             StandardDeviation=sd(PercentLive_pct[!is.na(PercentLive_pct)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_Y_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_Y_Stats$ShellType[MA_Y_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_Y_Stats$ShellType[MA_Y_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName then Year
MA_Y_Stats <- as.data.table(MA_Y_Stats[order(MA_Y_Stats$ManagedAreaName,
                                             MA_Y_Stats$Year,
                                             MA_Y_Stats$ShellType,
                                             MA_Y_Stats$SizeClass,
                                             MA_Y_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_Y_Stats, paste0(out_dir,"/Percent_Live/Oyster_PrcLive_MA_Yr_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_Y_Stats)

# Create summary statistics for each managed area based on Month intervals.
MA_M_Stats <- oysterraw[oysterraw$nyrpar=="PercentLive_pct",] %>%
   group_by(AreaID, ManagedAreaName, Month, nyrpar,
            LiveDate_Qualifier, SizeClass,
            HabitatClassification) %>%
   dplyr::summarize(N_Data=length(PercentLive_pct[!is.na(PercentLive_pct)]),
             Min=min(PercentLive_pct[!is.na(PercentLive_pct)]),
             Max=max(PercentLive_pct[!is.na(PercentLive_pct)]),
             Median=median(PercentLive_pct[!is.na(PercentLive_pct)]),
             Mean=mean(PercentLive_pct[!is.na(PercentLive_pct)]),
             StandardDeviation=sd(PercentLive_pct[!is.na(PercentLive_pct)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_M_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_M_Stats$ShellType[MA_M_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_M_Stats$ShellType[MA_M_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName then Month
MA_M_Stats <- as.data.table(MA_M_Stats[order(MA_M_Stats$ManagedAreaName,
                                             MA_M_Stats$Month,
                                             MA_M_Stats$ShellType,
                                             MA_M_Stats$SizeClass,
                                             MA_M_Stats$HabitatType), ])
# Writes summary statistics to file
fwrite(MA_M_Stats, paste0(out_dir,"/Percent_Live/Oyster_PrcLive_MA_Mo_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_M_Stats)

# Create summary overall statistics for each managed area.
MA_Ov_Stats <- oysterraw[oysterraw$nyrpar=="PercentLive_pct",] %>%
   group_by(AreaID, ManagedAreaName, nyrpar,
            LiveDate_Qualifier, SizeClass,
            HabitatClassification) %>%
   dplyr::summarize(N_Years=length(unique(
     LiveDate[!is.na(LiveDate) & !is.na(PercentLive_pct)])),
             SufficientData=ifelse(N_Years>=5, TRUE, FALSE),
             EarliestLiveDate=min(LiveDate[!is.na(PercentLive_pct)]),
             LatestLiveDate=max(LiveDate[!is.na(PercentLive_pct)]),
             LastSampleDate=max(SampleDate),
             N_Data=length(PercentLive_pct[!is.na(PercentLive_pct)]),
             Min=min(PercentLive_pct[!is.na(PercentLive_pct)]),
             Max=max(PercentLive_pct[!is.na(PercentLive_pct)]),
             Median=median(PercentLive_pct[!is.na(PercentLive_pct)]),
             Mean=mean(PercentLive_pct[!is.na(PercentLive_pct)]),
             StandardDeviation=sd(PercentLive_pct[!is.na(PercentLive_pct)]),
             Programs=paste(sort(unique(ProgramName), decreasing=FALSE),
                              collapse=', '),
             ProgramIDs=paste(sort(unique(ProgramID), decreasing=FALSE),
                              collapse=', '))
setnames(MA_Ov_Stats, c("nyrpar", "LiveDate_Qualifier",
                        "HabitatClassification"),
         c("ParameterName", "ShellType", "HabitatType"))
MA_Ov_Stats$ShellType[MA_Ov_Stats$ShellType=="Exact"] <- "Live Oyster Shells"
MA_Ov_Stats$ShellType[MA_Ov_Stats$ShellType=="Estimate"] <- "Dead Oyster Shells"
# Puts the data in order based on ManagedAreaName
MA_Ov_Stats <- as.data.table(MA_Ov_Stats[order(MA_Ov_Stats$ManagedAreaName,
                                               MA_Ov_Stats$ShellType,
                                               MA_Ov_Stats$SizeClass,
                                               MA_Ov_Stats$HabitatType), ])

# Replaces blank ProgramIDs with NA (missing values)
MA_Ov_Stats$ProgramIDs <- replace(MA_Ov_Stats$ProgramIDs,
                                  MA_Ov_Stats$ProgramIDs=="", NA)
MA_Ov_Stats$Programs <- replace(MA_Ov_Stats$Programs,
                                  MA_Ov_Stats$Programs=="", NA)
# Write overall statistics to file
fwrite(MA_Ov_Stats, paste0(out_dir,"/Percent_Live/Oyster_PrcLive_MA_Overall_Stats.txt"),
       sep="|")
# Removes variable storing data to improve computer memory
rm(MA_Ov_Stats)

# LiveDate Threshold -----------------------------------------------------
oysterraw <- oysterraw[oysterraw$LiveDate>=1960,]

for(i in unique(oysterraw$ManagedAreaName)){
      oysterraw[ManagedAreaName==i & !is.na(LiveDate), `:=`
                (RelYear=(LiveDate-min(LiveDate))+1)]
}
```



# Functions

Sets universal them for plots and creates functions that are used to create figures and data files from data subsets and GLMM models.
The functions are:

1. diagnosticplots
+ Creates panel of summary plots for each analysis

2. meplots
+ Creates and saves plots for density and live percent

3. modresults
+ Takes input data and model results for density and live percent.
+ Adds model results to compilation variable.
+ Send data and model results to diagnosticplots and meplots

4. meplotssh
+ Creates and saves plots for shell height

5. modresultssh
+ Takes input data and model results for shell height.
+ Adds model results to compilation variable.
+ Send data and model results to diagnosticplots and meplotssh

```{r Functions, eval=F, echo=T}
plot_theme <- theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        text=element_text(family="Arial"),
        plot.title=element_text(hjust=0.5, size=12, color="#314963"),
        plot.subtitle=element_text(hjust=0.5, size=10, color="#314963"),
        legend.title=element_text(size=10),
        legend.text = element_text(hjust = 0),
        axis.title.x = element_text(size=10, margin = margin(t = 5, r = 0,
                                                             b = 10, l = 0)),
        axis.title.y = element_text(size=10, margin = margin(t = 0, r = 10,
                                                             b = 0, l = 0)),
        axis.text=element_text(size=10),
        axis.text.x=element_text(angle = -45, hjust = 0))

plot_jitter <- position_jitter(width = 0.1, height = 0.1, seed=42)
#Function to save diagnostic plots
diagnosticplots <- function(model, indicator, managedarea, sizeclass="",
                            historical=FALSE){
  ind <- case_when(str_detect(indicator, "ercent") ~ "Pct",
                   str_detect(indicator, "ensity") ~ "Den",
                   str_detect(indicator, "^S|^s") ~ "SH")
  
  ma <- managedarea
  
  if(sizeclass != ""){
    size <- case_when(str_detect(sizeclass, "25") &
                        str_detect(sizeclass, "75") ~ "25to75", 
                      str_detect(sizeclass, "35") &
                        str_detect(sizeclass, "75") ~ "35to75",
                      str_detect(sizeclass, "25")==FALSE &
                        str_detect(sizeclass, "75") ~ "o75", TRUE ~ "raw")
    sizelab <- case_when(str_detect(sizeclass, "25") &
                           str_detect(sizeclass, "75") ~ "25-75mm", 
                         str_detect(sizeclass, "35") &
                           str_detect(sizeclass, "75") ~ "35-75mm",
                         str_detect(sizeclass, "25")==FALSE &
                           str_detect(sizeclass, "75") ~ "\u2265 75mm", 
                         TRUE ~ "raw")
  }
  
  #Save diagnostic plot(s) of chains
  diag <- plot(model, plot=FALSE)
  
  title <- textGrob(paste0(ma, " (", ind, " ", sizelab, ")"),
                    just="left",
                    gp=gpar(fontsize=10))
  
  diag[[1]] <- gtable_add_rows(
    diag[[1]],
    heights=grobHeight(title)+unit(5, "mm"),
    pos=0
  )
  
  diag[[1]] <- gtable_add_grob(
    diag[[1]],
    title,
    clip="off",
    1, 1, 1, 1)
  
  if(class(try(diag[[2]], silent=TRUE)) != "try-error"){
    diag[[2]] <- gtable_add_rows(
      diag[[2]],
      heights=grobHeight(title)+unit(5, "mm"),
      pos=0
    )
  }
  
  if(class(try(diag[[3]], silent=TRUE)) != "try-error"){
    diag[[3]] <- gtable_add_rows(
      diag[[3]],
      heights=grobHeight(title)+unit(5, "mm"),
      pos=0
    )
  }
  
  #save chains plots
  jpeg(filename=paste0("output/Figures/", ind, "_AllDates_GLMM_", ma,
                       "_PDistandMChains_", ifelse(sizeclass != "",
                                                   paste0(size, "_"), ""),
                       ifelse(historical==TRUE, "hist_", "_"),
                       Sys.Date(), ".png"),
       width=6,
       height=ifelse(length(diag)==1, 6, ifelse(length(diag)==2, 12, 18)),
       units="in", quality=100, res=300)
  print(grid.arrange(grobs=diag, ncol=1))
  dev.off()
  
  #Save posterior predictive check plot
  postpc <- tryCatch(pp_check(model),
                     error=function(e) NA)
  k <- 1001
  
  while(is.na(postpc)==TRUE & k <= 1000){
    postpc <- tryCatch(pp_check(model), 
                       error=function(e) NA)
    k <- k+1
  }
  
  if(!is.na(postpc)){
    postpc <- postpc +
      labs(title=paste0(ind, "_AllDates_GLMM_", ma, "_PPcheck_",
                        ifelse(sizeclass != "", paste0(size, "_"), ""),
                        ifelse(historical==TRUE, "_hist_", "_"),
                        Sys.Date(), ".png"))
    
    ma_short <- MA_All[ManagedAreaName==ma, Abbreviation]
    
    ggsave(paste0("output/Figures/", ind, "_AllDates_GLMM_", ma_short, "_PPcheck_",
                  ifelse(sizeclass != "", paste0(size, "_"), ""),
                  ifelse(historical==TRUE, "_hist_", "_"), Sys.Date(),
                  ".png"),
           postpc,
           width=6,
           height=6,
           units="in",
           dpi=300)
  }
  
  print(paste0("Plots saved."))
  
}

# Save marginal effects plots
meplots <- function(models, data, indicator, managedarea, sizeclass="",
                    zoom=FALSE){
  ind <- case_when(str_detect(indicator, "ercent") ~ "Pct",
                   str_detect(indicator, "ensity") ~ "Den",
                   str_detect(indicator, "^S|^s") ~ "SH")
  
  ma <- managedarea
  
  if(sizeclass != ""){
    size <- case_when(str_detect(sizeclass, "25") &
                        str_detect(sizeclass, "75") ~ "25to75",
                      str_detect(sizeclass, "35") &
                        str_detect(sizeclass, "75") ~ "35to75",
                      str_detect(sizeclass, "25")==FALSE &
                        str_detect(sizeclass, "75") ~ "o75", TRUE ~ "raw")
    sizelab <- case_when(str_detect(sizeclass, "25") &
                           str_detect(sizeclass, "75") ~ "25-75mm",
                         str_detect(sizeclass, "35") &
                           str_detect(sizeclass, "75") ~ "35-75mm",
                         str_detect(sizeclass, "25")==FALSE &
                           str_detect(sizeclass, "75") ~ "\u2265 75mm",
                         TRUE ~ "raw")
  }
  
  
  
  
  if(ind=="Den"){ 
    nyrs <- max(data$LiveDate)-min(data$LiveDate)+1
    maxyr <- max(data$LiveDate)
    minyr <- min(data$LiveDate)
    if(grepl("Natural", unique(data$MA_plotlab))==TRUE){
      type <- "Natural"
    } else{
      type <- "Restored"
    }
    yrdiff <- unique(data$YearDiff)
    # Creates break intervals for plots based on number of years of data
    if(nyrs>=40){
      # Set breaks to every 10 years if more than 40 years of data
      brk <- 10
    }else if(nyrs<40 & nyrs>=20){
      # Set breaks to every 5 years if between 40 and 20 years of data
      brk <- 5
    }else if(nyrs<20 & nyrs>=12){
      # Set breaks to every 3 years if between 20 and 12 years of data
      brk <- 3
    }else if(nyrs<12 & nyrs>=8){
      # Set breaks to every 2 years if between 12 and 8 years of data
      brk <- 2
    }else if(nyrs<8){
      # Set breaks to every year if less than 8 years of data
      brk <- 1
    }else if(nyrs<3){
      brk <- 1
      maxyr <- maxyr + 1
      minyr <- minyr - 1
    }
    yrlist <- seq(minyr,maxyr,brk)
    # nbreaks <- ifelse(nyrs < 11, nyrs+1, 12)
    # breaks <- if(minyr==0){
    #   c(minyr, round(minyr+c(1:(nbreaks-2))*((nyrs/nbreaks) +
    #                                            (nyrs/nbreaks)/nbreaks)),
    #     maxyr)+1
    # } else{
    #   c(minyr, round(minyr+c(1:(nbreaks-2))*((nyrs/nbreaks) +
    #                                            (nyrs/nbreaks)/nbreaks)),
    #     maxyr)
    # }
    
    denplots <- plot(conditional_effects(models[[1]], re_formula=NULL),
                     plot=FALSE)
    
    plot1 <- ggplot() +
      {if("meanDen_int" %in% colnames(data)){
        geom_point(data=data, aes(x=LiveDate,
                                  y=meanDen_int), position=plot_jitter,
                   shape=21, size=2, color="#333333", fill="#cccccc",
                   alpha=1, inherit.aes=FALSE)
      } else{
        geom_point(data=data, aes(x=LiveDate,
                                  y=Density_m2), position=plot_jitter,
                   shape=21, size=2, color="#333333", fill="#cccccc",
                   alpha=1, inherit.aes=FALSE)
      }
      } +
      list(geom_ribbon(data=denplots$RelYear$data,
                       aes(x=RelYear+yrdiff, y=Density_m2,
                           ymin=lower__, ymax=upper__),
                       fill="#000099", alpha=0.1, inherit.aes=FALSE),
           geom_line(data=denplots$RelYear$data,
                     aes(x=RelYear+yrdiff,
                         y=estimate__),
                     color="#000099", lwd=0.75, inherit.aes=FALSE)) +
      scale_x_continuous(limits=c(minyr-0.25, maxyr+0.25),
                         breaks=yrlist) +
      plot_theme +
      {if("meanDen_int" %in% colnames(data)){
        labs(title="Oyster Density",
             subtitle=managedarea,
             x="Year",
             y=bquote('Estimated density ('*~m^{-2}*')'))
      }else{
        labs(title="Oyster Density",
             subtitle=managedarea,
             x="Year",
             y=bquote('Density ('*~m^{-2}*')'))
      }}
    # labs(title="Oyster Density",
    #      subtitle=managedarea,
    #      x="Year",
    #      y=ifelse("meanDen_int" %in% colnames(data),
    #                           "Estimated density (square meters)",
    #                           bquote('Richness (species/100'*~m^{2}*')')))
    
    
    ma_short <- MA_All[ManagedAreaName==ma, Abbreviation]
    
    ggsave(paste0("output/Density/Figures/Oyster_Dens_GLMM_", ma_short, "_", type,
                  ifelse(sizeclass != "", paste0(size), "_raw"), ".png"),
           plot1,
           width=8,
           height=4,
           units="in",
           dpi=200)
  }
  
  
  #Marginal effects plot including random effects for percent live
  if(ind=="Pct"){
    nyrs <- max(data$LiveDate)-min(data$LiveDate)+1
    maxyr <- max(data$LiveDate)
    minyr <- min(data$LiveDate)
    yrdiff <- unique(data$YearDiff)
    # Creates break intervals for plots based on number of years of data
    if(nyrs>=40){
      # Set breaks to every 10 years if more than 40 years of data
      brk <- 10
    }else if(nyrs<40 & nyrs>=20){
      # Set breaks to every 5 years if between 40 and 20 years of data
      brk <- 5
    }else if(nyrs<20 & nyrs>=12){
      # Set breaks to every 3 years if between 20 and 12 years of data
      brk <- 3
    }else if(nyrs<12 & nyrs>=8){
      # Set breaks to every 2 years if between 12 and 8 years of data
      brk <- 2
    }else if(nyrs<8){
      # Set breaks to every year if less than 8 years of data
      brk <- 1
    }else if(nyrs<3){
      brk <- 1
      maxyr <- maxyr + 1
      minyr <- minyr - 1
    }
    yrlist <- seq(minyr,maxyr,brk)
    # nbreaks <- ifelse(nyrs < 11, nyrs+1, 12)
    # breaks <- if(minyr==0){
    #   c(minyr, round(minyr+c(1:(nbreaks-2))*((nyrs/nbreaks) +
    #                                            (nyrs/nbreaks)/nbreaks)),
    #     maxyr)+1
    # } else{
    #   c(minyr, round(minyr+c(1:(nbreaks-2))*((nyrs/nbreaks) +
    #                                            (nyrs/nbreaks)/nbreaks)),
    #     maxyr)
    # }
    
    set.seed(987)
    pctplots <- plot(conditional_effects(models[[1]], re_formula=NULL),
                     plot=FALSE)
    
    plot1 <- ggplot() +
      geom_point(data=data, aes(x=LiveDate,
                                y=100*PercentLive_dec), position=plot_jitter,
                 shape=21, size=2, color="#333333", fill="#cccccc",
                 alpha=1, inherit.aes=FALSE) +
      {if(names(pctplots$RelYear$data[2])=="PercentLive_dec"){
        list(geom_ribbon(data=pctplots$RelYear$data,
                         aes(x=RelYear+yrdiff,
                             y=100*PercentLive_dec, ymin=100*lower__,
                             ymax=100*upper__), fill="#000099",
                         alpha=0.1, inherit.aes=FALSE),
             geom_line(data=pctplots$RelYear$data,
                       aes(x=RelYear+yrdiff,
                           y=100*estimate__), color="#000099",
                       lwd=0.75, inherit.aes=FALSE))
      } else{
        list(geom_ribbon(data=pctplots$RelYear$data,
                         aes(x=RelYear+yrdiff,
                             y=100*LiveObs, ymin=100*lower__,
                             ymax=100*upper__), fill="#000099",
                         alpha=0.1, inherit.aes=FALSE),
             geom_line(data=pctplots$RelYear$data,
                       aes(x=RelYear+yrdiff,
                           y=100*estimate__), color="#000099",
                       lwd=0.75, inherit.aes=FALSE))
      }} +
      scale_x_continuous(limits=c(minyr-0.25, maxyr+0.25),
                         breaks=yrlist) +
      plot_theme +
      theme(legend.text=element_text(size=10), 
            legend.title=element_text(size=10)) +
      {
        if(managedarea=="Lemon Bay Aquatic Preserve"){
          labs(title="Percent of Live vs. Dead Oysters",
               subtitle=managedarea,
               x="Year",
               y="Live vs. dead (%)")
        } else {
          labs(title="Oyster Percent Live Cover",
               subtitle=managedarea,
               x="Year",
               y="Live cover (%)")
        }
      }
    
    ma_short <- MA_All[ManagedAreaName==ma, Abbreviation]
    
    ggsave(paste0("output/Percent_Live/Figures/Oyster_PrcLive_GLMM_", ma_short,
                  "_raw.png"),
           plot1,
           width=8,
           height=4,
           units="in",
           dpi=200)
    
    #Plot of modeled mean percent live
    if("Region" %in% names(pctplots)){
      meanPct <- pctplots$Region$data
      setnames(meanPct, "effect1__", "Region")
      
      meanpctplot <- ggplot(meanPct, aes(x=Region, y=estimate__,
                                         ymin=lower__, ymax=upper__)) +
        geom_pointinterval(fill="black", size=3,
                           fatten_point=4, shape=21,
                           color="black") +
        labs(title="Oyster Percent Live Cover",
             subtitle=managedarea,
             y="Live cover (%)",
             fill=NULL) +
        plot_theme +
        theme(legend.text=element_text(size=10), 
              legend.title=element_text(size=10))
      
      ma_short <- MA_All[ManagedAreaName==ma, Abbreviation]
      
      ggsave(paste0("output/Percent_Live/Figures/Oyster_PrcLive_GLMM_", ma_short,
                    "_raw_MeanRes.png"),
             meanpctplot,
             width=8,
             height=4,
             units="in",
             dpi=200)
    }
    
    #Plot of RelYear * Region interaction
    if("RelYear:Region" %in% names(pctplots)){
      pctplots$RelYear$data$RelYear <-
        pctplots$RelYear$data$RelYear-
        (min(pctplots$RelYear$data$RelYear)-1)
      RelYrbyRegion <- pctplots$`RelYear:Region`
      
      
      intplot <- RelYrbyRegion +
        geom_point(data=data, aes(x=RelYear-(min(RelYear)-1),
                                  y=PercentLive_dec,
                                  fill=Region),
                   alpha=0.5, shape=21, size=3, color="black",
                   inherit.aes=FALSE) +
        scale_x_continuous(breaks=breaks,
                           labels=c(yrlist[breaks])) +
        labs(title=ma,
             x="Year",
             y="Proportion live",
             fill="Region") +
        plot_theme +
        theme(legend.text=element_text(size=12), 
              legend.title=element_text(size=13), 
              legend.position="none") +
        facet_wrap(~ Region, ncol=3, scales="free")
      
      ma_short <- MA_All[ManagedAreaName==ma, Abbreviation]
      
      ggsave(paste0("output/Percent_Live/Figures/Oyster_PrcLive_GLMM_", ma_short,
                    "_raw.png"),
             intplot,
             width=10,
             height=10,
             units="in",
             dpi=300)
    }
  }
}

# Create model results tables and save diagnostic plots
modresults <- function(datafile, models, indicator, meplotzoom=FALSE){
  for(m in seq_along(models)){
    modelobj <- models[[m]]
    sizeclass <- ifelse(str_detect(modelobj$file, "25to75|seed"),
                        "25-75mm", 
                        ifelse(str_detect(modelobj$file, "35to75|seed"),
                               "35-75mm",
                               ifelse(str_detect(modelobj$file,
                                                 "o75|market"),
                                      ">75mm", "NA")))
    oyres_i <- setDT(broom.mixed::tidy(modelobj))
    #tidy() does not like that parameter values have underscores for
    #some reason, so the resulting table is incomplete
    
    if(nrow(oyres_i[effect=="fixed", ])-nrow(summary(modelobj)$fixed)==-1){
      missingrow <- data.table(effect="fixed",
                               component="cond",
                               #not sure what "cond" means in the tidy summary.
                               group=NA,
                               term=rownames(summary(modelobj)$fixed)[2],
                               estimate=summary(modelobj)$fixed$Estimate[2],
                               std.error=summary(modelobj)$fixed$Est.Error[2],
                               conf.low=summary(modelobj)$fixed$`l-95% CI`[2],
                               conf.high=summary(modelobj)$fixed$`u-95% CI`[2])
      oyres_i <- rbind(oyres_i, missingrow) %>% arrange(effect, group)
    }
    
    oyres_i[, `:=` (indicator=indicator,
                    managed_area=unique(datafile$ManagedAreaName),
                    habitat_class=unique(datafile$HabitatClassification),
                    size_class=sizeclass,
                    live_date_qual=ifelse(
                      str_detect(modelobj$file, "_hist"),
                      "Estimate", "Exact"),
                    n_programs=if(
                      class(try(datafile$LiveDate_Qualifier)) !=
                      "try-error"){
                      length(
                        unique(
                          datafile[LiveDate_Qualifier==
                                     ifelse(
                                       str_detect(
                                         modelobj$file,
                                         "_hist"),
                                       "Estimate",
                                       "Exact"),
                                   ProgramID]))
                    } else{length(unique(datafile[, ProgramID]))},
                    programs=if(class(try(
                      datafile$LiveDate_Qualifier)) != "try-error"){
                      list(unique(datafile[LiveDate_Qualifier==
                                             ifelse(
                                               str_detect(
                                                 modelobj$file,
                                                 "_hist"),
                                               "Estimate",
                                               "Exact"),
                                           ProgramID]))
                    } else{list(unique(datafile[, ProgramID]))},
                    filename=modelobj$file)]
    oysterresults <<- rbind(oysterresults, oyres_i)
    
    # Save diagnostic plots
    #diagnosticplots(modelobj, indicator,
    #unique(datafile$ManagedAreaName), sizeclass,
    #ifelse(str_detect(modelobj$file, "_hist"), TRUE, FALSE))  
  }
  
  # Save marginal effects plots
  meplots(models, datafile, indicator, unique(datafile$ManagedAreaName),
          sizeclass, meplotzoom)
}
# Marginal effects plots for shell height (attempt to combine models into one plot)
meplotssh <- function(models1, data1, sizeclass1="", models2, data2,
                      sizeclass2="", managedarea, indicator, zoom=FALSE){
  ind <- case_when(str_detect(indicator, "ercent") ~ "Pct",
                   str_detect(indicator, "ensity") ~ "Den",
                   str_detect(indicator, "^S|^s") ~ "SH")
  ma <- managedarea
  
  sizeclass1 <- unique(data1$SizeClass)
  sizeclass2 <- unique(data2$SizeClass)
  # Set size labels
  if(sizeclass1 != ""){
    size1 <- case_when(
      str_detect(sizeclass1, "25") & str_detect(sizeclass1, "75") ~ "25to75",
      str_detect(sizeclass1, "35") & str_detect(sizeclass1, "75") ~ "35to75",
      str_detect(sizeclass1, "25")==FALSE & str_detect(sizeclass1, "75") ~ "o75",
      TRUE ~ "raw")
    sizelab1 <- case_when(
      str_detect(sizeclass1, "25") & str_detect(sizeclass1, "75") ~ "25-75mm",
      str_detect(sizeclass1, "35") & str_detect(sizeclass1, "75") ~ "35-75mm",
      str_detect(sizeclass1, "25")==FALSE & str_detect(sizeclass1, "75") ~ "\u2265 75mm",
      TRUE ~ "raw")
  }
  if(sizeclass2 != ""){
    size2 <- case_when(
      str_detect(sizeclass2, "25") & str_detect(sizeclass2, "75") ~ "25to75",
      str_detect(sizeclass2, "35") & str_detect(sizeclass2, "75") ~ "35to75",
      str_detect(sizeclass2, "25")==FALSE & str_detect(sizeclass2, "75") ~ "o75",
      TRUE ~ "raw")
    sizelab2 <- case_when(
      str_detect(sizeclass2, "25") & str_detect(sizeclass2, "75") ~ "25-75mm",
      str_detect(sizeclass2, "35") & str_detect(sizeclass2, "75") ~ "35-75mm",
      str_detect(sizeclass2, "25")==FALSE & str_detect(sizeclass2, "75") ~ "\u2265 75mm",
      TRUE ~ "raw")
  }
  
  #Marginal effects plot including random effects
  ## Hist plot settings
  y_max <- round(max(data2[!is.na(ShellHeight_mm), ShellHeight_mm]), -0)+1
  y_breaks <- seq(0, 300, 50)
  y_labs <- seq(0, 300, 50)
  y_minor <- seq(0, 300, 25)
  ylim_upper <- ceiling(y_max/25)*25
  
  yrdiff1 <- unique(data1$YearDiff)
  yrdiff2 <- unique(data2$YearDiff)
  
  # function to set year breaks, type == "hist" or "live"
  set_breaks <- function(type, data1, data2){
    ldq <- ifelse(type=="hist", "Estimate", "Exact")
    
    maxyr <- max(data1[!is.na(LiveDate) & LiveDate_Qualifier==ldq, LiveDate],
                 data2[!is.na(LiveDate) & LiveDate_Qualifier==ldq, LiveDate])
    minyr <- min(data1[!is.na(LiveDate) & LiveDate_Qualifier==ldq, LiveDate],
                 data2[!is.na(LiveDate) & LiveDate_Qualifier==ldq, LiveDate])
    nyrs <- (maxyr)-(minyr)+1
    
    # Creates break intervals for plots based on number of years of data
    if(nyrs>=40){
      # Set breaks to every 10 years if more than 30 years of data
      brk <- 10
    }else if(nyrs<40 & nyrs>=20){
      # Set breaks to every 5 years if between 30 and 15 years of data
      brk <- 5
    }else if(nyrs<20 & nyrs>=12){
      # Set breaks to every 3 years if between 15 and 9 years of data
      brk <- 3
    }else if(nyrs<12 & nyrs>=8){
      # Set breaks to every 2 years if between 9 and 6 years of data
      brk <- 2
    }else if(nyrs<8 & nyrs>=3){
      # Set breaks to every year if less than 6 years of data
      brk <- 1
    }else if(nyrs<3){
      brk <- 1
      maxyr <- maxyr + 1
      minyr <- minyr - 1
    }
    return(list("seq" = seq(minyr,maxyr,brk),"maxyr" = maxyr, "minyr" = minyr))
  }
  
  yrlist_hist <- set_breaks(type = "hist", data1 = data1, data2 = data2)[["seq"]]
  maxyr_hist <- set_breaks(type = "hist", data1 = data1, data2 = data2)[["maxyr"]]
  minyr_hist <- set_breaks(type = "hist", data1 = data1, data2 = data2)[["minyr"]]
  yrlist_live <- set_breaks(type = "live", data1 = data1, data2 = data2)[["seq"]]
  maxyr_live <- set_breaks(type = "live", data1 = data1, data2 = data2)[["maxyr"]]
  minyr_live <- set_breaks(type = "live", data1 = data1, data2 = data2)[["minyr"]]
  
  ## Check data for Exact and Estimate
  n_hist1 <- nrow(data1[data1$LiveDate_Qualifier=="Estimate" &
                          !is.na(data1$ShellHeight_mm),])
  n_live1 <- nrow(data1[data1$LiveDate_Qualifier=="Exact" &
                          !is.na(data1$ShellHeight_mm),])
  n_hist2 <- nrow(data2[data2$LiveDate_Qualifier=="Estimate" &
                          !is.na(data2$ShellHeight_mm),])
  n_live2 <- nrow(data2[data2$LiveDate_Qualifier=="Exact" &
                          !is.na(data2$ShellHeight_mm),])
  
  set.seed(987)
  if(!is.null(models1)){
    liveplot_1 <- plot(conditional_effects(models1[[1]], re_formula=NULL), plot=FALSE)
  }
  
  if(!is.null(models2)){
    liveplot_2 <- plot(conditional_effects(models2[[1]], re_formula=NULL), plot=FALSE)
  }
  
  # Set boolean values for whether liveplot1&2 are available
  liveplot1_avail <- class(try(liveplot_1, silent=TRUE)) != "try-error"
  liveplot2_avail <- class(try(liveplot_2, silent=TRUE)) != "try-error"
  
  # Set ribbon transparency value
  a_ribb <- 0.2
  # Set size and shapes for plots
  p_shape <- c("size2"=24, "size1"=21)
  sizelab <- c("size2"=sizelab2, "size1"=sizelab1)
  
  check <- NA
  check1 <- NA
  check2 <- NA
  
  if(exists("present1")){
    check1 <- c("size1"="#00374f")
  } else{
    check1 <- c("size1"="#FFFFFF")
  }
  
  if(exists("present2")){
    check2 <- c("size2"="#0094b0")
  } else{
    check2 <- c("size2"="#FFFFFF")
  }
  p_color <- c(check2, check1)
  
  # Initial plots to set legends
  plot_leg <- ggplot() +
    {if(liveplot1_avail){
      list(geom_ribbon(data=liveplot_1$RelYear$data,
                       aes(x=RelYear+yrdiff1, y=ShellHeight_mm,
                           ymin=lower__, ymax=upper__,
                           fill="size1"), alpha=a_ribb),
           geom_line(data=liveplot_1$RelYear$data,
                     aes(x=RelYear+yrdiff1, y=estimate__, color="size1"),
                     lwd=0.75))
    }} +
    {if(liveplot2_avail){
      list(geom_ribbon(data=liveplot_2$RelYear$data,
                       aes(x=RelYear+yrdiff2, y=ShellHeight_mm,
                           ymin=lower__, ymax=upper__, 
                           fill="size2"), alpha=a_ribb),
           geom_line(data=liveplot_2$RelYear$data,
                     aes(x=RelYear+yrdiff2, y=estimate__, color="size2"),
                     lwd=0.75))
    }} +
    geom_point(data=data1[!is.na(RelYear) & !is.na(LiveDate), ],
               aes(x=LiveDate, y=ShellHeight_mm, shape="size1"),
               position=plot_jitter, size=2, color="#333333", fill="#cccccc",
               alpha=0.2, inherit.aes=FALSE) +
    geom_point(data=data2[!is.na(RelYear) & !is.na(LiveDate), ],
               aes(x=LiveDate, y=ShellHeight_mm, shape="size2"),
               position=plot_jitter, size=2, color="#333333", fill="#cccccc",
               alpha=0.2, inherit.aes=FALSE) +
    plot_theme +
    theme(legend.position="right") +
    scale_shape_manual(name="Shell heights",
                       values=p_shape,
                       labels=sizelab) +
    scale_color_manual(name="Shell heights",
                       values=p_color,
                       labels=sizelab) +
    scale_fill_manual(name="Shell heights",
                      values=p_color,
                      labels=sizelab)
  
  leg <-get_legend(plot_leg)
  rm(plot_leg)
  
  # Dead oyster shell plot
  plot1 <- ggplot() +
    geom_hline(yintercept=75, size=1, color="grey") +
    {if(n_hist1>0){
      geom_point(data=data1[!is.na(RelYear) &
                              !is.na(LiveDate) &
                              LiveDate_Qualifier=="Estimate", ],
                 aes(x=LiveDate, y=ShellHeight_mm, shape="size1"),
                 position=plot_jitter, size=2, color="#333333", fill="#cccccc",
                 alpha=0.2, inherit.aes=FALSE) 
    }} +
    {if(n_hist2>0){
      geom_point(data=data2[!is.na(RelYear) & !is.na(LiveDate) &
                              LiveDate_Qualifier=="Estimate", ],
                 aes(x=LiveDate, y=ShellHeight_mm, shape="size2"),
                 position=plot_jitter, size=2, color="#333333", fill="#cccccc",
                 alpha=0.2, inherit.aes=FALSE)
    }} +
    scale_x_continuous(limits=c(minyr_hist-0.25, maxyr_hist+0.25),
                       breaks=yrlist_hist) +
    scale_y_continuous(breaks=y_breaks,
                       labels=y_labs, minor_breaks=y_minor) +
    plot_theme +
    theme(plot.subtitle=element_text(hjust=0, size=10, color="#314963"),
          legend.position="none",
    ) +
    labs(subtitle="Dead Oyster Shells",
         x="Estimated year",
         y="Shell height (mm)") +
    scale_shape_manual(name="Shell heights",
                       values=c("size1"=21, "size2"=24),
                       labels=c(sizelab1, sizelab2)) +
    scale_color_manual(name="Shell heights",
                       values=c("size1"="#00374f", "size2"="#0094b0"),
                       labels=c(sizelab1, sizelab2)) +
    scale_fill_manual(name="Shell heights",
                      values=c("size1"="#00374f", "size2"="#0094b0"),
                      labels=c(sizelab1, sizelab2)) +
    coord_cartesian(ylim=c(0, ylim_upper))
  
  # Live oyster shell plot
  plot2 <- ggplot() +
    geom_hline(yintercept=75, size=1, color="grey") +
    {if(n_live1>0){
      geom_point(data=data1[!is.na(RelYear) & !is.na(LiveDate) &
                              LiveDate_Qualifier=="Exact", ],
                 aes(x=LiveDate, y=ShellHeight_mm, shape="size1"),
                 position=plot_jitter, size=2, color="#333333", fill="#cccccc",
                 alpha=0.2, inherit.aes=FALSE) 
    }} +
    {if(n_live2>0){
      geom_point(data=data2[!is.na(RelYear) & !is.na(LiveDate) &
                              LiveDate_Qualifier=="Exact", ],
                 aes(x=LiveDate, y=ShellHeight_mm, shape="size2"),
                 position=plot_jitter, size=2, color="#333333", fill="#cccccc",
                 alpha=0.2, inherit.aes=FALSE)
    }} +
    {if(liveplot1_avail){
      list(geom_ribbon(data=liveplot_1$RelYear$data,
                       aes(x=RelYear+yrdiff1, y=ShellHeight_mm,
                           ymin=lower__, ymax=upper__, fill="size1"),
                       alpha=a_ribb),
           geom_line(data=liveplot_1$RelYear$data,
                     aes(x=RelYear+yrdiff1, y=estimate__, color="size1"),
                     lwd=0.75))
    }} +
    {if(liveplot2_avail){
      list(geom_ribbon(data=liveplot_2$RelYear$data,
                       aes(x=RelYear+yrdiff2, y=ShellHeight_mm,
                           ymin=lower__, ymax=upper__, fill="size2"),
                       alpha=a_ribb),
           geom_line(data=liveplot_2$RelYear$data,
                     aes(x=RelYear+yrdiff2, y=estimate__, color="size2"),
                     lwd=0.75))
    }} +
    scale_x_continuous(limits=c(minyr_live-0.25, maxyr_live+0.25),
                       breaks=yrlist_live) +
    scale_y_continuous(breaks=y_breaks,
                       labels=y_labs, minor_breaks=y_minor) +
    plot_theme +
    theme(plot.subtitle=element_text(hjust=0, size=10, color="#314963"),
          legend.position="none",
          axis.text.y=element_blank(),  #remove y-axis labels
          axis.ticks.y=element_blank(),  #remove y-axis ticks
          axis.title.y=element_blank()   #removes y-axis title
    ) +
    labs(subtitle="Live Oyster Shells",
         x="Year",
         y="Shell height (mm)") +
    scale_shape_manual(name="Shell heights",
                       values=c("size1"=21, "size2"=24),
                       labels=c(sizelab1, sizelab2)) +
    scale_color_manual(name="Shell heights",
                       values=c("size1"="#00374f", "size2"="#0094b0"),
                       labels=c(sizelab1, sizelab2)) +
    scale_fill_manual(name="Shell heights",
                      values=c("size1"="#00374f", "size2"="#0094b0"),
                      labels=c(sizelab1, sizelab2)) +
    coord_cartesian(ylim=c(0, ylim_upper))
  
  # Set plot title
  plot_title <- ggplot() +
    labs(title="Oyster Size Class", subtitle=ma) +
    plot_theme +
    theme(plot.subtitle=element_text(hjust=0.5, size=10, color="#314963"),
          panel.border=element_blank(),
          panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(), axis.line=element_blank())
  
  plot_comb <- ggarrange(plot1, plot2, leg, nrow=1,
                         widths=c(0.46, 0.39, 0.15))
  
  plot_comb <- ggarrange(plot_title, plot_comb, ncol=1,
                         heights=c(0.125, 0.875))
  
  ma_abrev <- MA_All[ManagedAreaName==ma, Abbreviation]
  
  ggsave(paste0("output/Shell_Height/Figures/Oyster_SH_GLMM_", ma_abrev, ".png"),
         plot_comb,
         width=8,
         height=4,
         units="in",
         dpi=200,
         bg="white")
  rm(liveplot_1, liveplot_2)
}

# Marginal effects plots for shell height (attempt to combine models into one plot)
meplotssh <- function(models1, data1, sizeclass1="", models2, data2,
                      sizeclass2="", managedarea, indicator, zoom=FALSE){
  ind <- case_when(str_detect(indicator, "ercent") ~ "Pct",
                   str_detect(indicator, "ensity") ~ "Den",
                   str_detect(indicator, "^S|^s") ~ "SH")
  ma <- managedarea
  
  sizeclass1 <- unique(data1$SizeClass)
  sizeclass2 <- unique(data2$SizeClass)
  # Set size labels
  if(sizeclass1 != ""){
    size1 <- case_when(
      str_detect(sizeclass1, "25") & str_detect(sizeclass1, "75") ~ "25to75",
      str_detect(sizeclass1, "35") & str_detect(sizeclass1, "75") ~ "35to75",
      str_detect(sizeclass1, "25")==FALSE & str_detect(sizeclass1, "75") ~ "o75",
      TRUE ~ "raw")
    sizelab1 <- case_when(
      str_detect(sizeclass1, "25") & str_detect(sizeclass1, "75") ~ "25-75mm",
      str_detect(sizeclass1, "35") & str_detect(sizeclass1, "75") ~ "35-75mm",
      str_detect(sizeclass1, "25")==FALSE & str_detect(sizeclass1, "75") ~ "\u2265 75mm",
      TRUE ~ "raw")
  }
  if(sizeclass2 != ""){
    size2 <- case_when(
      str_detect(sizeclass2, "25") & str_detect(sizeclass2, "75") ~ "25to75",
      str_detect(sizeclass2, "35") & str_detect(sizeclass2, "75") ~ "35to75",
      str_detect(sizeclass2, "25")==FALSE & str_detect(sizeclass2, "75") ~ "o75",
      TRUE ~ "raw")
    sizelab2 <- case_when(
      str_detect(sizeclass2, "25") & str_detect(sizeclass2, "75") ~ "25-75mm",
      str_detect(sizeclass2, "35") & str_detect(sizeclass2, "75") ~ "35-75mm",
      str_detect(sizeclass2, "25")==FALSE & str_detect(sizeclass2, "75") ~ "\u2265 75mm",
      TRUE ~ "raw")
  }
  
  #Marginal effects plot including random effects
  ## Hist plot settings
  y_max <- round(max(data2[!is.na(ShellHeight_mm), ShellHeight_mm]), -0)+1
  y_breaks <- seq(0, 300, 50)
  y_labs <- seq(0, 300, 50)
  y_minor <- seq(0, 300, 25)
  ylim_upper <- ceiling(y_max/25)*25
  
  yrdiff1 <- unique(data1$YearDiff)
  yrdiff2 <- unique(data2$YearDiff)
  
  # function to set year breaks, type == "hist" or "live"
  set_breaks <- function(type, data1, data2){
    ldq <- ifelse(type=="hist", "Estimate", "Exact")
    
    maxyr <- max(data1[!is.na(LiveDate) & LiveDate_Qualifier==ldq, LiveDate],
                 data2[!is.na(LiveDate) & LiveDate_Qualifier==ldq, LiveDate])
    minyr <- min(data1[!is.na(LiveDate) & LiveDate_Qualifier==ldq, LiveDate],
                 data2[!is.na(LiveDate) & LiveDate_Qualifier==ldq, LiveDate])
    nyrs <- (maxyr)-(minyr)+1
    
    # Creates break intervals for plots based on number of years of data
    if(nyrs>=40){
      # Set breaks to every 10 years if more than 30 years of data
      brk <- 10
    }else if(nyrs<40 & nyrs>=20){
      # Set breaks to every 5 years if between 30 and 15 years of data
      brk <- 5
    }else if(nyrs<20 & nyrs>=12){
      # Set breaks to every 3 years if between 15 and 9 years of data
      brk <- 3
    }else if(nyrs<12 & nyrs>=8){
      # Set breaks to every 2 years if between 9 and 6 years of data
      brk <- 2
    }else if(nyrs<8 & nyrs>=3){
      # Set breaks to every year if less than 6 years of data
      brk <- 1
    }else if(nyrs<3){
      brk <- 1
      maxyr <- maxyr + 1
      minyr <- minyr - 1
    }
    return(list("seq" = seq(minyr,maxyr,brk),"maxyr" = maxyr, "minyr" = minyr))
  }
  
  yrlist_hist <- set_breaks(type = "hist", data1 = data1, data2 = data2)[["seq"]]
  maxyr_hist <- set_breaks(type = "hist", data1 = data1, data2 = data2)[["maxyr"]]
  minyr_hist <- set_breaks(type = "hist", data1 = data1, data2 = data2)[["minyr"]]
  yrlist_live <- set_breaks(type = "live", data1 = data1, data2 = data2)[["seq"]]
  maxyr_live <- set_breaks(type = "live", data1 = data1, data2 = data2)[["maxyr"]]
  minyr_live <- set_breaks(type = "live", data1 = data1, data2 = data2)[["minyr"]]
  
  ## Check data for Exact and Estimate
  n_hist1 <- nrow(data1[data1$LiveDate_Qualifier=="Estimate" &
                          !is.na(data1$ShellHeight_mm),])
  n_live1 <- nrow(data1[data1$LiveDate_Qualifier=="Exact" &
                          !is.na(data1$ShellHeight_mm),])
  n_hist2 <- nrow(data2[data2$LiveDate_Qualifier=="Estimate" &
                          !is.na(data2$ShellHeight_mm),])
  n_live2 <- nrow(data2[data2$LiveDate_Qualifier=="Exact" &
                          !is.na(data2$ShellHeight_mm),])
  
  set.seed(987)
  if(!is.null(models1)){
    liveplot_1 <- plot(conditional_effects(models1[[1]], re_formula=NULL), plot=FALSE)
  }
  
  if(!is.null(models2)){
    liveplot_2 <- plot(conditional_effects(models2[[1]], re_formula=NULL), plot=FALSE)
  }
  
  # Set boolean values for whether liveplot1&2 are available
  liveplot1_avail <- class(try(liveplot_1, silent=TRUE)) != "try-error"
  liveplot2_avail <- class(try(liveplot_2, silent=TRUE)) != "try-error"
  
  # Set ribbon transparency value
  a_ribb <- 0.2
  # Set size and shapes for plots
  p_shape <- c("size2"=24, "size1"=21)
  sizelab <- c("size2"=sizelab2, "size1"=sizelab1)
  
  check <- NA
  check1 <- NA
  check2 <- NA
  
  if(exists("present1")){
    check1 <- c("size1"="#00374f")
  } else{
    check1 <- c("size1"="#FFFFFF")
  }
  
  if(exists("present2")){
    check2 <- c("size2"="#0094b0")
  } else{
    check2 <- c("size2"="#FFFFFF")
  }
  p_color <- c(check2, check1)
  
  # Initial plots to set legends
  plot_leg <- ggplot() +
    {if(liveplot1_avail){
      list(geom_ribbon(data=liveplot_1$RelYear$data,
                       aes(x=RelYear+yrdiff1, y=ShellHeight_mm,
                           ymin=lower__, ymax=upper__,
                           fill="size1"), alpha=a_ribb),
           geom_line(data=liveplot_1$RelYear$data,
                     aes(x=RelYear+yrdiff1, y=estimate__, color="size1"),
                     lwd=0.75))
    }} +
    {if(liveplot2_avail){
      list(geom_ribbon(data=liveplot_2$RelYear$data,
                       aes(x=RelYear+yrdiff2, y=ShellHeight_mm,
                           ymin=lower__, ymax=upper__, 
                           fill="size2"), alpha=a_ribb),
           geom_line(data=liveplot_2$RelYear$data,
                     aes(x=RelYear+yrdiff2, y=estimate__, color="size2"),
                     lwd=0.75))
    }} +
    geom_point(data=data1[!is.na(RelYear) & !is.na(LiveDate), ],
               aes(x=LiveDate, y=ShellHeight_mm, shape="size1"),
               position=plot_jitter, size=2, color="#333333", fill="#cccccc",
               alpha=0.2, inherit.aes=FALSE) +
    geom_point(data=data2[!is.na(RelYear) & !is.na(LiveDate), ],
               aes(x=LiveDate, y=ShellHeight_mm, shape="size2"),
               position=plot_jitter, size=2, color="#333333", fill="#cccccc",
               alpha=0.2, inherit.aes=FALSE) +
    plot_theme +
    theme(legend.position="right") +
    scale_shape_manual(name="Shell heights",
                       values=p_shape,
                       labels=sizelab) +
    scale_color_manual(name="Shell heights",
                       values=p_color,
                       labels=sizelab) +
    scale_fill_manual(name="Shell heights",
                      values=p_color,
                      labels=sizelab)
  
  leg <-get_legend(plot_leg)
  rm(plot_leg)
  
  # Dead oyster shell plot
  plot1 <- ggplot() +
    geom_hline(yintercept=75, size=1, color="grey") +
    {if(n_hist1>0){
      geom_point(data=data1[!is.na(RelYear) &
                              !is.na(LiveDate) &
                              LiveDate_Qualifier=="Estimate", ],
                 aes(x=LiveDate, y=ShellHeight_mm, shape="size1"),
                 position=plot_jitter, size=2, color="#333333", fill="#cccccc",
                 alpha=0.2, inherit.aes=FALSE) 
    }} +
    {if(n_hist2>0){
      geom_point(data=data2[!is.na(RelYear) & !is.na(LiveDate) &
                              LiveDate_Qualifier=="Estimate", ],
                 aes(x=LiveDate, y=ShellHeight_mm, shape="size2"),
                 position=plot_jitter, size=2, color="#333333", fill="#cccccc",
                 alpha=0.2, inherit.aes=FALSE)
    }} +
    scale_x_continuous(limits=c(minyr_hist-0.25, maxyr_hist+0.25),
                       breaks=yrlist_hist) +
    scale_y_continuous(breaks=y_breaks,
                       labels=y_labs, minor_breaks=y_minor) +
    plot_theme +
    theme(plot.subtitle=element_text(hjust=0, size=10, color="#314963"),
          legend.position="none",
    ) +
    labs(subtitle="Dead Oyster Shells",
         x="Estimated year",
         y="Shell height (mm)") +
    scale_shape_manual(name="Shell heights",
                       values=c("size1"=21, "size2"=24),
                       labels=c(sizelab1, sizelab2)) +
    scale_color_manual(name="Shell heights",
                       values=c("size1"="#00374f", "size2"="#0094b0"),
                       labels=c(sizelab1, sizelab2)) +
    scale_fill_manual(name="Shell heights",
                      values=c("size1"="#00374f", "size2"="#0094b0"),
                      labels=c(sizelab1, sizelab2)) +
    coord_cartesian(ylim=c(0, ylim_upper))
  
  # Live oyster shell plot
  plot2 <- ggplot() +
    geom_hline(yintercept=75, size=1, color="grey") +
    {if(n_live1>0){
      geom_point(data=data1[!is.na(RelYear) & !is.na(LiveDate) &
                              LiveDate_Qualifier=="Exact", ],
                 aes(x=LiveDate, y=ShellHeight_mm, shape="size1"),
                 position=plot_jitter, size=2, color="#333333", fill="#cccccc",
                 alpha=0.2, inherit.aes=FALSE) 
    }} +
    {if(n_live2>0){
      geom_point(data=data2[!is.na(RelYear) & !is.na(LiveDate) &
                              LiveDate_Qualifier=="Exact", ],
                 aes(x=LiveDate, y=ShellHeight_mm, shape="size2"),
                 position=plot_jitter, size=2, color="#333333", fill="#cccccc",
                 alpha=0.2, inherit.aes=FALSE)
    }} +
    {if(liveplot1_avail){
      list(geom_ribbon(data=liveplot_1$RelYear$data,
                       aes(x=RelYear+yrdiff1, y=ShellHeight_mm,
                           ymin=lower__, ymax=upper__, fill="size1"),
                       alpha=a_ribb),
           geom_line(data=liveplot_1$RelYear$data,
                     aes(x=RelYear+yrdiff1, y=estimate__, color="size1"),
                     lwd=0.75))
    }} +
    {if(liveplot2_avail){
      list(geom_ribbon(data=liveplot_2$RelYear$data,
                       aes(x=RelYear+yrdiff2, y=ShellHeight_mm,
                           ymin=lower__, ymax=upper__, fill="size2"),
                       alpha=a_ribb),
           geom_line(data=liveplot_2$RelYear$data,
                     aes(x=RelYear+yrdiff2, y=estimate__, color="size2"),
                     lwd=0.75))
    }} +
    scale_x_continuous(limits=c(minyr_live-0.25, maxyr_live+0.25),
                       breaks=yrlist_live) +
    scale_y_continuous(breaks=y_breaks,
                       labels=y_labs, minor_breaks=y_minor) +
    plot_theme +
    theme(plot.subtitle=element_text(hjust=0, size=10, color="#314963"),
          legend.position="none",
          axis.text.y=element_blank(),  #remove y-axis labels
          axis.ticks.y=element_blank(),  #remove y-axis ticks
          axis.title.y=element_blank()   #removes y-axis title
    ) +
    labs(subtitle="Live Oyster Shells",
         x="Year",
         y="Shell height (mm)") +
    scale_shape_manual(name="Shell heights",
                       values=c("size1"=21, "size2"=24),
                       labels=c(sizelab1, sizelab2)) +
    scale_color_manual(name="Shell heights",
                       values=c("size1"="#00374f", "size2"="#0094b0"),
                       labels=c(sizelab1, sizelab2)) +
    scale_fill_manual(name="Shell heights",
                      values=c("size1"="#00374f", "size2"="#0094b0"),
                      labels=c(sizelab1, sizelab2)) +
    coord_cartesian(ylim=c(0, ylim_upper))
  
  # Set plot title
  plot_title <- ggplot() +
    labs(title="Oyster Size Class", subtitle=ma) +
    plot_theme +
    theme(plot.subtitle=element_text(hjust=0.5, size=10, color="#314963"),
          panel.border=element_blank(),
          panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(), axis.line=element_blank())
  
  plot_comb <- ggarrange(plot1, plot2, leg, nrow=1,
                         widths=c(0.46, 0.39, 0.15))
  
  plot_comb <- ggarrange(plot_title, plot_comb, ncol=1,
                         heights=c(0.125, 0.875))
  
  ma_abrev <- MA_All[ManagedAreaName==ma, Abbreviation]
  
  ggsave(paste0("output/Shell_Height/Figures/Oyster_SH_GLMM_", ma_abrev, ".png"),
         plot_comb,
         width=8,
         height=4,
         units="in",
         dpi=200,
         bg="white")
  rm(liveplot_1, liveplot_2)
}


# Create model results tables and save diagnostic plots
modresultssh <- function(datafile1, models1, datafile2, models2, indicator,
                         meplotzoom=FALSE){
  datafile1$SizeClass[datafile1$SizeClass=="25to75mm" &
                        datafile1$MA_plotlab==
                        "St. Martins Marsh Aquatic Preserve_Natural"] <-
    "35-75mm"
  sizeclass1 <- unique(datafile1$SizeClass)
  for(m in seq_along(models1)){
    modelobj <- models1[[m]]
    oyres_i <- setDT(broom.mixed::tidy(modelobj))
    #tidy() does not like that parameter values have underscores
    #for some reason, so the resulting table is incomplete
    
    if(nrow(oyres_i[effect=="fixed", ])-nrow(summary(modelobj)$fixed)==-1){
      missingrow <- data.table(effect="fixed",
                               component="cond",
                               #not sure what "cond" means in the tidy summary.
                               group=NA,
                               term=rownames(summary(modelobj)$fixed)[2],
                               estimate=summary(modelobj)$fixed$Estimate[2],
                               std.error=summary(modelobj)$fixed$Est.Error[2],
                               conf.low=summary(modelobj)$fixed$`l-95% CI`[2],
                               conf.high=summary(modelobj)$fixed$`u-95% CI`[2])
      oyres_i <- rbind(oyres_i, missingrow) %>% arrange(effect, group)
    }
    
    setDT(oyres_i)
    oyres_i[, `:=` (indicator=indicator,
                    managed_area=unique(datafile1$ManagedAreaName),
                    habitat_class=unique(datafile1$HabitatClassification),
                    size_class=sizeclass1,
                    live_date_qual=ifelse(
                      str_detect(
                        modelobj$file, "_hist"), "Estimate",
                      "Exact"),
                    n_programs=if(class(
                      try(datafile1$LiveDate_Qualifier))!="try-error"){
                      length(unique(
                        datafile1[LiveDate_Qualifier==
                                    ifelse(str_detect(
                                      modelobj$file, "_hist"),
                                      "Estimate", "Exact"),
                                  ProgramID]))
                    } else{length(unique(datafile1[, ProgramID]))},
                    programs=if(class(try(
                      datafile1$LiveDate_Qualifier)) != "try-error"){
                      list(unique(
                        datafile1[LiveDate_Qualifier==
                                    ifelse(
                                      str_detect(
                                        modelobj$file,
                                        "_hist"),
                                      "Estimate",
                                      "Exact"),
                                  ProgramID]))
                    } else{list(unique(datafile1[, ProgramID]))},
                    filename=modelobj$file)]
    
    oysterresults <<- rbind(oysterresults, oyres_i)
    
    # Save diagnostic plots
    #diagnosticplots(modelobj, indicator,
    #unique(datafile$ManagedAreaName), sizeclass,
    #ifelse(str_detect(modelobj$file, "_hist"), TRUE, FALSE))  
  }
  
  datafile2$SizeClass[datafile2$SizeClass=="25to75mm" &
                        datafile2$MA_plotlab==
                        "St. Martins Marsh Aquatic Preserve_Natural"] <- "35-75mm"
  sizeclass2 <- unique(datafile2$SizeClass)
  
  for(m in seq_along(models2)){
    modelobj <- models2[[m]]
    oyres_i <- setDT(broom.mixed::tidy(modelobj))
    #tidy() does not like that parameter values have underscores for
    #some reason, so the resulting table is incomplete
    
    if(nrow(oyres_i[effect=="fixed", ])-nrow(summary(modelobj)$fixed)==-1){
      missingrow <- data.table(effect="fixed",
                               component="cond",
                               #not sure what "cond" means in the tidy summary.
                               group=NA,
                               term=rownames(summary(modelobj)$fixed)[2],
                               estimate=summary(modelobj)$fixed$Estimate[2],
                               std.error=summary(modelobj)$fixed$Est.Error[2],
                               conf.low=summary(modelobj)$fixed$`l-95% CI`[2],
                               conf.high=summary(modelobj)$fixed$`u-95% CI`[2])
      oyres_i <- rbind(oyres_i, missingrow) %>% arrange(effect, group)
    }
    
    oyres_i <- oyres_i %>%
      mutate(
        indicator = indicator,
        managed_area = unique(datafile2$ManagedAreaName),
        habitat_class = unique(datafile2$HabitatClassification),
        size_class = sizeclass2,
        live_date_qual = if_else(
          str_detect(modelobj$file, "_hist"), "Estimate", "Exact"
        ),
        n_programs = if (class(try(datafile2$LiveDate_Qualifier)) != "try-error") {
          datafile2 %>%
            filter(LiveDate_Qualifier == if_else(str_detect(modelobj$file, "_hist"), "Estimate", "Exact")) %>%
            pull(ProgramID) %>%
            unique() %>%
            length()
        } else {
          datafile2 %>%
            pull(ProgramID) %>%
            unique() %>%
            length()
        },
        programs = if (class(try(datafile2$LiveDate_Qualifier)) != "try-error") {
          list(datafile2 %>%
                 filter(LiveDate_Qualifier == if_else(str_detect(modelobj$file, "_hist"), "Estimate", "Exact")) %>%
                 pull(ProgramID) %>%
                 unique())
        } else {
          list(datafile2 %>% pull(ProgramID) %>% unique())
        },
        filename = modelobj$file
      )
    oysterresults <<- rbind(oysterresults, oyres_i)
    
    # Save diagnostic plots
    #diagnosticplots(modelobj, indicator,
    #unique(datafile$ManagedAreaName), sizeclass,
    #ifelse(str_detect(modelobj$file, "_hist"), TRUE, FALSE))  
  }
  
  # Save marginal effects plots
  meplotssh(models1, datafile1, sizeclass1, models2, datafile2, sizeclass2,
            unique(datafile1$ManagedAreaName), indicator, meplotzoom)
}
```



# Oyster Shell Height Analysis

Subsets data for that which is related to shell height. The data is further subset for each managed area and shell size class. Appropriate GLMMs are called from file for each shell size class, or are created if they don't exist. Data and models are then sent to the modresultssh function to create figures and save data.

```{r ShellHeight, eval=F, echo=T}
# Parallel, num cores setup
ncores <- 4
nchains <- 4
threads <- 10
iter <- 3000
warmup <- 1000

# At least 5 years of data are required in order to run model analyses
# Function checks N years of data, returns T or F
suff_years <- function(data){length(unique(data$Year))>=5}

#summarize shell height data
sh_all_sum <- summarySE(oysterraw[!is.na(ShellHeight_mm), ],
                        measurevar='ShellHeight_mm',
                        groupvars=c('ManagedAreaName', 'LiveDate_Qualifier',
                                    'LiveDate'))



## Apalachicola Bay Aquatic Preserve_Natural ----------------------------------------

#Exclude the five samples that don't have counts less than the "NumberMeasured"
#value for the corresponding program (see variable exploration graphs in the
#25to75mm section for the rationale and graphs for this step.)
numValves <- unique(oysterraw[, c("ProgramID", "RelYear", "counts",
                                   "QuadIdentifier", "Subtidal", "QuadSize_m2",
                                   "LiveDate_Qualifier", "NumberMeasured_n")])
exclude_samps <- subset(numValves, numValves$NumberMeasured_n=="20" &
                          numValves$counts > 19)$QuadIdentifier
ab_sho25 <- oysterraw[!is.na(ShellHeight_mm) & 
                         ShellHeight_mm >= 25 &
                         MA_plotlab=="Apalachicola Bay Aquatic Preserve_Natural" & 
                         QuadIdentifier %in% setdiff(
                           oysterraw[!is.na(ShellHeight_mm) &
                                        ManagedAreaName==
                                        "Apalachicola Bay Aquatic Preserve",
                                      QuadIdentifier], exclude_samps), ]

saveRDS(ab_sho25, paste0('output/model_results/data/ab_sho25_', Sys.Date(), '.rds'))


### abap-25 to 75mm -------------------------------------------------------

ab_sh25to75 <- ab_sho25[ShellHeight_mm < 75, ]
saveRDS(ab_sh25to75, paste0('output/model_results/data/ab_sh25to75_', Sys.Date(), '.rds'))

if(suff_years(subset(ab_sh25to75, ab_sh25to75$LiveDate_Qualifier!="Estimate"))){
  ab_sh25to75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=25, ub=75) ~
                            RelYear+QuadSize_m2+(1 | UniversalReefID),
                          data=subset(ab_sh25to75, ab_sh25to75$LiveDate_Qualifier!="Estimate"),
                          family=gaussian, cores=ncores,
                          control=list(adapt_delta=0.995, max_treedepth=20),
                          iter=iter, warmup=warmup, chains=nchains, thin=3, seed=5699,
                          backend="rstan", threads=threading(threads),
                          file="output/model_results/GLMMs/ab_sh25to75_glmm4b.rds")
  
  models1 <- list(ab_sh25to75_glmm)
} else {models1 <- NULL}

# Create model results tables and save diagnostic plots
data1 <- ab_sh25to75


### ABAP->75mm ------------------------------------------------------------

ab_sho75 <- ab_sho25[ShellHeight_mm >= 75, ]

saveRDS(ab_sho75, paste0('output/model_results/data/ab_sho75_', Sys.Date(), '.rds'))

if(suff_years(subset(ab_sho75, ab_sho75$LiveDate_Qualifier!="Estimate"))){
  ab_sho75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=75, ub=250) ~
                         RelYear+(1 | UniversalReefID),
                       data=subset(ab_sho75, 
                                   ab_sho75$LiveDate_Qualifier!="Estimate"), 
                       family=gaussian, cores=ncores,
                       control= list(adapt_delta=0.995, max_treedepth=20),
                       iter=iter, warmup=warmup, chains=nchains, thin=3, seed=3639,
                       backend="rstan", threads=threading(threads),
                       file="output/model_results/GLMMs/ab_sho75_glmm4b.rds")
  
  models2 <- list(ab_sho75_glmm)
} else {models2 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data2 <- ab_sho75
modresultssh(data1, models1, data2, models2, "Size class", meplotzoom=FALSE)

## Apalachicola National Estuarine Research Reserve_Natural -------------------

an_sho25 <- oysterraw[!is.na(ShellHeight_mm) & 
                        !is.na(LiveDate) &
                        ShellHeight_mm >= 25 &
                        MA_plotlab==
                        "Apalachicola National Estuarine Research Reserve_Natural" & 
                        QuadIdentifier %in%
                        setdiff(oysterraw[!is.na(ShellHeight_mm) &
                                            ManagedAreaName==
                                            "Apalachicola National Estuarine Research Reserve",
                                          QuadIdentifier], exclude_samps), ]

saveRDS(an_sho25, paste0('output/model_results/data/an_sho25_', Sys.Date(), '.rds'))


### ANERR-25 to 75mm -------------------------------------------------------

an_sh25to75 <- subset(an_sho25, an_sho25$ShellHeight_mm < 75)

saveRDS(an_sh25to75, paste0('output/model_results/data/an_sh25to75_',
                            Sys.Date(), '.rds'))

if(suff_years(subset(an_sh25to75, an_sh25to75$LiveDate_Qualifier!="Estimate"))){
  an_sh25to75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=25, ub=75) ~
                            RelYear+QuadSize_m2+(1 | UniversalReefID),
                          data=subset(an_sh25to75, an_sh25to75$LiveDate_Qualifier!="Estimate"),
                          family=gaussian, cores=ncores,
                          control=list(adapt_delta=0.995, max_treedepth=20),
                          iter=iter, warmup=warmup, chains=nchains, thin=3, seed=5699,
                          backend="rstan", threads=threading(threads),
                          file="output/model_results/GLMMs/an_sh25to75_glmm4b.rds")
  
  models1 <- list(an_sh25to75_glmm)
} else {models1 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data1 <- an_sh25to75

### ANERR->75mm -------------------------------------------------------

an_sho75 <- an_sho25[ShellHeight_mm >= 75, ]

saveRDS(an_sho75, paste0('output/model_results/data/an_sho75_', Sys.Date(), '.rds'))

if(suff_years(subset(an_sho75, an_sho75$LiveDate_Qualifier!="Estimate"))){
  an_sho75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=75, ub=250) ~
                         RelYear+(1 | UniversalReefID),
                       data=subset(an_sho75, an_sho75$LiveDate_Qualifier!=
                                     "Estimate"), family=gaussian, cores=ncores,
                       control= list(adapt_delta=0.995, max_treedepth=20),
                       iter=iter, warmup=warmup, chains=nchains, thin=3, seed=3639,
                       backend="rstan", threads=threading(threads),
                       file="output/model_results/GLMMs/an_sho75_glmm4b.rds")
  models2 <- list(an_sho75_glmm)
} else {models2 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data2 <- an_sho75
#modresults(data, models, "Size class", meplotzoom=TRUE)
modresultssh(data1, models1, data2, models2, "Size class", meplotzoom=FALSE)

## Estero Bay Aquatic Preserve_Natural ---------------------------------------

eb_sho25 <- oysterraw[!is.na(ShellHeight_mm) & 
                        ShellHeight_mm >= 25 &
                        MA_plotlab=="Estero Bay Aquatic Preserve_Natural", ]

saveRDS(eb_sho25, paste0('output/model_results/data/eb_sho25_', Sys.Date(), '.rds'))


### EBAP-25 to 75mm -------------------------------------------------------

eb_sh25to75 <- subset(eb_sho25, eb_sho25$ShellHeight_mm < 75)
eb_sh25to75 <- eb_sh25to75[!is.na(eb_sh25to75$QuadSize_m2),]

saveRDS(eb_sh25to75, paste0('output/model_results/data/eb_sh25to75_',
                            Sys.Date(), '.rds'))

# Does not update models because this subset of data have NA for QuadSize_m2 values
if(suff_years(subset(eb_sh25to75,eb_sh25to75$LiveDate_Qualifier=="Exact"))){
  eb_sh25to75_glmm <- brm(formula=ShellHeight_mm ~
                            RelYear+QuadSize_m2+(0+RelYear | UniversalReefID),
                          data=subset(eb_sh25to75,
                                      eb_sh25to75$LiveDate_Qualifier=="Exact"),
                          family=gaussian, cores=ncores,
                          control= list(adapt_delta=0.995, max_treedepth=20),
                          iter=iter, warmup=warmup, chains=nchains, thin=3, seed=6881,
                          backend="rstan", threads=threading(threads),
                          file="output/model_results/GLMMs/eb_sh25to75_glmm5.rds")
  
  models1 <- list(eb_sh25to75_glmm)
} else {models1 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data1 <- eb_sh25to75

### EBAP->75mm -------------------------------------------------------

eb_sho75 <- eb_sho25[ShellHeight_mm >= 75, ]

saveRDS(eb_sho75, paste0('output/model_results/data/eb_sho75_', Sys.Date(), '.rds'))

if(suff_years(subset(eb_sho75, eb_sho75$LiveDate_Qualifier=="Exact"))){
  eb_sho75_glmm <- brm(formula=ShellHeight_mm ~
                         RelYear+(1 | UniversalReefID),
                       data=subset(eb_sho75, eb_sho75$LiveDate_Qualifier=="Exact"),
                       family=gaussian, cores=ncores,
                       control=list(adapt_delta=0.995, max_treedepth=20), iter=iter,
                       warmup=warmup, chains=nchains, thin=3, seed=3138,
                       backend="rstan", threads=threading(threads),
                       file="output/model_results/GLMMs/eb_sho75_glmm4.rds")
  models2 <- list(eb_sho75_glmm)
} else {models2 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data2 <- eb_sho75

modresultssh(data1, models1, data2, models2, "Size class", meplotzoom=FALSE)

## Guana River Marsh Aquatic Preserve_Natural ---------------------------------

grm_sho25 <- oysterraw[!is.na(ShellHeight_mm) & 
                         ShellHeight_mm >= 25 &
                         MA_plotlab==
                         "Guana River Marsh Aquatic Preserve_Natural", ]

saveRDS(grm_sho25, paste0('output/model_results/data/grm_sho25_',
                          Sys.Date(), '.rds'))


### GRMAP-25 to 75mm -------------------------------------------------------

grm_sh25to75 <- subset(grm_sho25, grm_sho25$ShellHeight_mm < 75)

saveRDS(grm_sh25to75, paste0('output/model_results/data/grm_sh25to75_',
                             Sys.Date(), '.rds'))



if(suff_years(subset(grm_sh25to75, grm_sh25to75$LiveDate_Qualifier=="Exact"))){
  # NumberMeasred_n contains NA, removed from formula
  grm_sh25to75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=25, ub=75) ~
                             RelYear+(1 | UniversalReefID),
                           data=subset(grm_sh25to75,
                                       grm_sh25to75$LiveDate_Qualifier=="Exact"),
                           family=gaussian, cores=ncores,
                           control= list(adapt_delta=0.8, max_treedepth=10),
                           iter=iter, warmup=warmup, chains=nchains, thin=3,
                           seed=3457, backend="rstan", threads=threading(threads),
                           file="output/model_results/GLMMs/grm_sh25to75_glmm4.rds")
  
  models1 <- list(grm_sh25to75_glmm)
} else {models1 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data1 <- grm_sh25to75

### GRMAP->75mm -------------------------------------------------------

grm_sho75 <- grm_sho25[ShellHeight_mm >= 75, ]

saveRDS(grm_sho75, paste0('output/model_results/data/grm_sho75_',
                          Sys.Date(), '.rds'))

if(suff_years(subset(grm_sho75, grm_sho75$LiveDate_Qualifier=="Exact"))){
  grm_sho75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=75, ub=250) ~
                          RelYear+(1 | UniversalReefID),
                        data=subset(grm_sho75,
                                    grm_sho75$LiveDate_Qualifier=="Exact"),
                        family=gaussian, cores=ncores,
                        control= list(adapt_delta=0.8, max_treedepth=10),
                        iter=iter, warmup=warmup, chains=nchains, thin=3,
                        seed=4352, backend="rstan", threads=threading(threads),
                        file="output/model_results/GLMMs/grm_sho75_glmm4.rds")
  models2 <- list(grm_sho75_glmm)
} else {models2 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data2 <- grm_sho75
modresultssh(data1, models1, data2, models2, "Size class", meplotzoom=FALSE)

## Guana Tolomato Matanzas National Estuarine Research Reserve_Natural --------

gtmn_sho25 <- oysterraw[!is.na(ShellHeight_mm) & 
                          ShellHeight_mm >= 25 &
                          MA_plotlab==
                          "Guana Tolomato Matanzas National Estuarine Research Reserve_Natural", ]

saveRDS(gtmn_sho25, paste0('output/model_results/data/gtmn_sho25_',
                           Sys.Date(), '.rds'))

### GTMNERR-25 to 75mm -------------------------------------------------------

gtmn_sh25to75 <- subset(gtmn_sho25, gtmn_sho25$ShellHeight_mm < 75)

saveRDS(gtmn_sh25to75, paste0('output/model_results/data/gtmn_sh25to75_',
                              Sys.Date(), '.rds'))

if(suff_years(subset(gtmn_sh25to75, gtmn_sh25to75$LiveDate_Qualifier != "Estimate"))){
  gtmn_sh25to75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=25, ub=75) ~
                              RelYear+(1 | UniversalReefID),
                            data=subset(gtmn_sh25to75,
                                        gtmn_sh25to75$LiveDate_Qualifier != "Estimate"),
                            family=gaussian, cores=ncores,
                            control=list(adapt_delta=0.8, max_treedepth=20),
                            iter=iter, warmup=warmup, chains=nchains, thin=3,
                            seed=7844, backend="rstan", threads=threading(threads),
                            file="output/model_results/GLMMs/gtmn_sh25to75_glmm5.rds")
  
  models1 <- list(gtmn_sh25to75_glmm)
} else {models1 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data1 <- gtmn_sh25to75

### GTMNERR->75mm -------------------------------------------------------

gtmn_sho75 <- gtmn_sho25[ShellHeight_mm >= 75, ]

saveRDS(gtmn_sho75, paste0('output/model_results/data/gtmn_sho75_',
                           Sys.Date(), '.rds'))

if(suff_years(subset(gtmn_sho75, gtmn_sho75$LiveDate_Qualifier != "Estimate"))){
  gtmn_sho75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=75, ub=250) ~
                           RelYear + (1 | UniversalReefID),
                         data=subset(gtmn_sho75,
                                     gtmn_sho75$LiveDate_Qualifier != "Estimate"),
                         family=gaussian,
                         cores=ncores, control=list(adapt_delta=0.995, max_treedepth=20),
                         iter=iter, warmup=warmup, chains=nchains, thin=3,
                         seed=5332, backend="rstan", threads=threading(threads),
                         file="output/model_results/GLMMs/gtmn_sho75_glmm6.rds")
  models2 <- list(gtmn_sho75_glmm)
} else {models2 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data2 <- gtmn_sho75
modresultssh(data1, models1, data2, models2, "Size class", meplotzoom=FALSE)

## Indian River-Vero Beach to Ft. Pierce Aquatic Preserve_Natural -------------
irvbfp_sho25 <- oysterraw[!is.na(ShellHeight_mm) & 
                            ShellHeight_mm >= 25 &
                            MA_plotlab==
                            "Indian River-Vero Beach to Ft. Pierce Aquatic Preserve_Natural", ]

saveRDS(irvbfp_sho25, paste0('output/model_results/data/irvbfp_sho25_',
                             Sys.Date(), '.rds'))


### IRVBFPAP-25 to 75mm -------------------------------------------------------

irvbfp_sh25to75 <- subset(irvbfp_sho25, irvbfp_sho25$ShellHeight_mm < 75)

saveRDS(irvbfp_sh25to75, paste0('output/model_results/data/irvbfp_sh25to75_',
                                Sys.Date(), '.rds'))

if(suff_years(subset(irvbfp_sh25to75, irvbfp_sh25to75$LiveDate_Qualifier != "Estimate"))){
  irvbfp_sh25to75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=25, ub=75) ~ 
                                RelYear+(1 | UniversalReefID),
                              data=subset(irvbfp_sh25to75,
                                          irvbfp_sh25to75$LiveDate_Qualifier != "Estimate"),
                              family=gaussian, cores=ncores,
                              control=list(adapt_delta=0.8, max_treedepth=20),
                              iter=iter, warmup=warmup, chains=nchains, thin=3,
                              seed=7844, backend="rstan", threads=threading(threads),
                              file="output/model_results/GLMMs/irvbfp_sh25to75_glmm.rds")
  
  models1 <- list(irvbfp_sh25to75_glmm)
} else {models1 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data1 <- irvbfp_sh25to75

### IRVBFPAP->75mm -------------------------------------------------------

irvbfp_sho75 <- irvbfp_sho25[ShellHeight_mm >= 75, ]

saveRDS(irvbfp_sho75, paste0('output/model_results/data/irvbfp_sho75_',
                             Sys.Date(), '.rds'))

if(suff_years(subset(irvbfp_sho75, irvbfp_sho75$LiveDate_Qualifier != "Estimate"))){
  irvbfp_sho75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=75, ub=250) ~
                             RelYear + (1 | UniversalReefID),
                           data=subset(irvbfp_sho75,
                                       irvbfp_sho75$LiveDate_Qualifier != "Estimate"),
                           family=gaussian,
                           cores=ncores, control=list(adapt_delta=0.995, max_treedepth=20),
                           iter=iter, warmup=warmup, chains=nchains, thin=3,
                           seed=5332, backend="rstan", threads=threading(threads),
                           file="output/model_results/GLMMs/irvbfp_sho75_glmm.rds")
  models2 <- list(irvbfp_sho75_glmm)
} else {models2 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data2 <- irvbfp_sho75
modresultssh(data1, models1, data2, models2, "Size class", meplotzoom=FALSE)

## Lemon Bay Aquatic Preserve_Natural ---------------------------------------

lb_sho25 <- oysterraw[!is.na(ShellHeight_mm) & 
                        ShellHeight_mm >= 25 &
                        MA_plotlab=="Lemon Bay Aquatic Preserve_Natural", ]

saveRDS(lb_sho25, paste0('output/model_results/data/lb_sho25_',
                         Sys.Date(), '.rds'))

### LBAP-25 to 75mm -------------------------------------------------------

lb_sh25to75 <- subset(lb_sho25, lb_sho25$ShellHeight_mm < 75)

saveRDS(lb_sh25to75, paste0('output/model_results/data/lb_sh25to75_', Sys.Date(), '.rds'))

if(suff_years(subset(lb_sh25to75, lb_sh25to75$LiveDate_Qualifier != "Estimate"))){
  lb_sh25to75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=25, ub=75) ~
                            RelYear+(1 | UniversalReefID),
                          data=subset(lb_sh25to75,
                                      lb_sh25to75$LiveDate_Qualifier != "Estimate"),
                          family=gaussian, cores=ncores,
                          control=list(adapt_delta=0.8, max_treedepth=20),
                          iter=iter, warmup=warmup, chains=nchains, thin=3,
                          seed=7844, backend="rstan", threads=threading(threads),
                          file="output/model_results/GLMMs/lb_sh25to75_glmm.rds")
  
  models1 <- list(lb_sh25to75_glmm)
} else {models1 <- NULL}

# Create model results tables and save diagnostic plots and marginal effects plots
data1 <- lb_sh25to75

### LBAP->75mm -------------------------------------------------------

lb_sho75 <- lb_sho25[ShellHeight_mm >= 75, ]

saveRDS(lb_sho75, paste0('output/model_results/data/lb_sho75_', Sys.Date(), '.rds'))

if(suff_years(subset(lb_sho75, lb_sho75$LiveDate_Qualifier != "Estimate"))){
  lb_sho75_glmm <- brm(formula=ShellHeight_mm | trunc(lb=25, ub=75) ~
                            RelYear+(1 | UniversalReefID),
                          data=subset(lb_sho75,
                                      lb_sho75$LiveDate_Qualifier != "Estimate"),
                          family=gaussian, cores=ncores,
                          control=list(adapt_delta=0.8, max_treedepth=20),
                          iter=iter, warmup=warmup, chains=nchains, thin=3,
                          seed=7844, backend="rstan", threads=threading(threads),
                          file="output/model_results/GLMMs/lb_sho75_glmm.rds")
  
  models2 <- list(lb_sho75_glmm)
} else {models2 <- NULL}

#Important: note that time-averaging is not accounted for in the model fit for
#the data on shell height >75mm. The measurement error approach I was taking
#did not result in any models that converged, possibly because the combination
#of the data and degree of measurement error leads to multiple possible
#solutions. This means the model reported in this section makes the unrealistic
#assumption that the estimated sample ages are exactly correct.

# Create model results tables and save diagnostic plots and marginal effects plots
data2 <- lb_sho75
modresultssh(data1, models1, data2, models2, "Size class", meplotzoom=FALSE)
```



# Density Analysis

Subsets data for that which is related to density. The data is further subset for each managed area. Appropriate GLMMs are called from file for each shell size class, or are created if they don't exist. Data and models are then sent to the modresults function to create figures and save data.

```{r Density, eval=F, echo=T}
oysterraw$YearDiff <- oysterraw$LiveDate-oysterraw$RelYear
# #Make a collapsed version of the oysterraw table for density
oysterraw_den <- oysterraw[, c("ProgramID", "ProgramName", "LocationID",
                               "ProgramLocationID", "QuadIdentifier",
                               "ReefIdentifier", "LiveDate",
                               "LiveDate_Qualifier", "SampleDate", "Year",
                               "Month", "ManagedAreaName", "Region",
                               "SurveyMethod", "HabitatClassification",
                               "QuadSize_m2", "MADup", "Density_m2",
                               "Number_of_Oysters_Counted_Total_Count",
                               "Number_of_Oysters_Counted_Live_Count",
                               "Number_of_Oysters_Counted_Dead_Count",
                               "ObsIndex", "UniversalReefID",
                               "MA_plotlab", "Subtidal", "RelYear", "YearDiff")]
oysterraw_den[!is.na(Density_m2), DensIndex := ObsIndex]
oysterraw_den[!is.na(Number_of_Oysters_Counted_Total_Count), NTotIndex := ObsIndex]
oysterraw_den[!is.na(Number_of_Oysters_Counted_Live_Count), NLiveIndex := ObsIndex]
oysterraw_den[!is.na(Number_of_Oysters_Counted_Dead_Count), NDeadIndex := ObsIndex]
oysterraw_den[, ObsIndex := NULL]

oysterraw_den <- unique(oysterraw_den)
oysterraw_den <- oysterraw_den %>%
  dplyr::group_by(ProgramID, ProgramName, LocationID, ProgramLocationID,
                  QuadIdentifier, ReefIdentifier, LiveDate,
                  LiveDate_Qualifier, SampleDate, Year, Month,
                  ManagedAreaName, Region, SurveyMethod,
                  HabitatClassification, QuadSize_m2, MADup, UniversalReefID, 
                  MA_plotlab, Subtidal) %>%
  tidyr::fill(Density_m2, Number_of_Oysters_Counted_Total_Count,
              Number_of_Oysters_Counted_Live_Count,
              Number_of_Oysters_Counted_Dead_Count,
              DensIndex, NTotIndex, NLiveIndex, NDeadIndex) %>%
  tidyr::fill(Density_m2, Number_of_Oysters_Counted_Total_Count,
              Number_of_Oysters_Counted_Live_Count,
              Number_of_Oysters_Counted_Dead_Count,
              DensIndex, NTotIndex, NLiveIndex, NDeadIndex,
              .direction='up') %>%
  dplyr::distinct()

oysterraw_den <- subset(oysterraw_den, !is.na(oysterraw_den$Density_m2) |
                          !is.na(oysterraw_den$Number_of_Oysters_Counted_Total_Count) |
                          !is.na(oysterraw_den$Number_of_Oysters_Counted_Live_Count) |
                          !is.na(oysterraw_den$Number_of_Oysters_Counted_Dead_Count) |
                          !is.na(oysterraw_den$DensIndex) |
                          !is.na(oysterraw_den$NTotIndex) |
                          !is.na(oysterraw_den$NLiveIndex) |
                          !is.na(oysterraw_den$NDeadIndex))
setDT(oysterraw_den)

#Remove NAs in Density_m2 column
oysterraw_den <- subset(oysterraw_den, !is.na(oysterraw_den$Density_m2))

#Summarize density data by managed area
den_all_sum <- summarySE(oysterraw_den, measurevar='Density_m2',
                         groupvars=c('ManagedAreaName', 'Year'))

## Raw density results -----------------------------------------------------


### Apalachicola Bay Aquatic Preserve_Natural ----------------------------------------

ab_n <- subset(oysterraw_den,
               oysterraw_den$MA_plotlab==
                 "Apalachicola Bay Aquatic Preserve_Natural")
ab_n[, Density_m2 := as.integer(round(Density_m2))]
saveRDS(ab_n, paste0('output/model_results/data/ab_n_', Sys.Date(), '.rds'))

ab_den_glmm <- brm(formula=Density_m2 ~
                     RelYear+(0+RelYear | UniversalReefID), data=ab_n,
                   family=negbinomial, cores=ncores,
                   control= list(adapt_delta=0.995, max_treedepth=20),
                   iter=iter,
                   warmup=warmup, chains=nchains, init=0, thin=3, seed=5512,
                   backend="rstan", threads=threading(threads),
                   file="output/model_results/GLMMs/ab_den_glmm9.rds")

# ab_den_glmm <- update(ab_den_glmm, 
#                       newdata = ab_n,
#                       family=negbinomial, cores=ncores,
#                       control= list(adapt_delta=0.995, max_treedepth=20),
#                       iter=iter,
#                       warmup=warmup, chains=nchains, init=0, thin=3, seed=5512,
#                       backend="rstan", threads=threading(threads),
#                       file="output/model_results/GLMMs/ab_den_glmm9.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- ab_n
models <- list(ab_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)


### Apalachicola National Estuarine Research Reserve_Natural ----------------------------------------

an_n <- subset(oysterraw_den,
               oysterraw_den$MA_plotlab==
                 "Apalachicola National Estuarine Research Reserve_Natural")
an_n[, Density_m2 := as.integer(round(Density_m2))]
saveRDS(an_n, paste0('output/model_results/data/an_n_', Sys.Date(), '.rds'))

an_den_glmm <- brm(formula=Density_m2 ~
                     RelYear+Subtidal+(0+RelYear | UniversalReefID),
                   data=an_n, family=zero_inflated_negbinomial, cores=ncores,
                   control= list(adapt_delta=0.995, max_treedepth=20), iter=iter,
                   warmup=warmup, chains=nchains, init=0, thin=3, seed=4677,
                   backend="rstan", threads=threading(threads),
                   file="output/model_results/GLMMs/an_den_glmm11.rds")

# an_den_glmm <- update(an_den_glmm, 
#                       newdata = an_n,
#                       family=zero_inflated_negbinomial, cores=ncores,
#                       control= list(adapt_delta=0.995, max_treedepth=20), iter=iter,
#                       warmup=warmup, chains=nchains, init=0, thin=3, seed=4677,
#                       backend="rstan", threads=threading(threads),
#                       file="output/model_results/GLMMs/an_den_glmm11.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- an_n
models <- list(an_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)

### Estero Bay Aquatic Preserve_Natural ----------------------------------------

eb_n <- subset(oysterraw_den,
               oysterraw_den$MA_plotlab=="Estero Bay Aquatic Preserve_Natural")
eb_n[, Density_m2 := as.integer(round(Density_m2))]
saveRDS(eb_n, paste0('output/model_results/data/eb_n_', Sys.Date(), '.rds'))

eb_den_glmm <- brm(formula=Density_m2 ~
                     RelYear+(1 | UniversalReefID), data=eb_n,
                   family=zero_inflated_negbinomial, cores=ncores,
                   control= list(adapt_delta=0.995, max_treedepth=20), iter=iter,
                   warmup=warmup, chains=nchains, init=0, thin=3, seed=1298,
                   backend="rstan", threads=threading(threads),
                   file="output/model_results/GLMMs/eb_den_glmm10.rds")

# eb_den_glmm <- update(eb_den_glmm, 
#                       newdata = eb_n,
#                       family=zero_inflated_negbinomial, cores=ncores,
#                       control= list(adapt_delta=0.995, max_treedepth=20), iter=iter,
#                       warmup=warmup, chains=nchains, init=0, thin=3, seed=1298,
#                       backend="rstan", threads=threading(threads),
#                       file="output/model_results/GLMMs/eb_den_glmm10.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- eb_n
models <- list(eb_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)

### Guana River Marsh Aquatic Preserve_Natural ----------------------------------------

grm_n <- subset(oysterraw_den,
                oysterraw_den$MA_plotlab==
                  "Guana River Marsh Aquatic Preserve_Natural")
grm_n[, Density_m2 := as.integer(round(Density_m2))]
saveRDS(grm_n, paste0('output/model_results/data/grm_n_',
                      Sys.Date(), '.rds'))

grm_den_glmm <- brm(formula=Density_m2 ~
                      RelYear+(1 | UniversalReefID), data=grm_n,
                    family=zero_inflated_negbinomial, cores=2,
                    control= list(adapt_delta=0.995, max_treedepth=20),
                    iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
                    seed=9875, backend="rstan", threads=threading(threads),
                    file="output/model_results/GLMMs/grm_den_glmm6.rds")

# grm_den_glmm <- update(grm_den_glmm, 
#                        newdata = grm_n,
#                        family=zero_inflated_negbinomial, cores=2,
#                        control= list(adapt_delta=0.995, max_treedepth=20),
#                        iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                        seed=9875, backend="rstan", threads=threading(threads),
#                        file="output/model_results/GLMMs/grm_den_glmm6.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- grm_n
models <- list(grm_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)

### Guana Tolomato Matanzas National Estuarine Research Reserve_Natural ----------------------------------------

gtmn_n <- subset(oysterraw_den,
                 oysterraw_den$MA_plotlab==
                   "Guana Tolomato Matanzas National Estuarine Research Reserve_Natural")
gtmn_n[, Density_m2 := as.integer(round(Density_m2))]
saveRDS(gtmn_n, paste0('output/model_results/data/gtmn_n_', Sys.Date(), '.rds'))

gtmn_den_glmm <- brm(formula=Density_m2 ~
                       RelYear+(1 | UniversalReefID),
                     data=gtmn_n, family=zero_inflated_negbinomial, cores=ncores,
                     control= list(adapt_delta=0.995, max_treedepth=20),
                     iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
                     seed=3647, backend="rstan", threads=threading(threads),
                     file="output/model_results/GLMMs/gtmn_den_glmm18.rds")

# gtmn_den_glmm <- update(gtmn_den_glmm, 
#                         newdata = gtmn_n,
#                         family=zero_inflated_negbinomial, cores=ncores,
#                         control= list(adapt_delta=0.995, max_treedepth=20),
#                         iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                         seed=3647, backend="rstan", threads=threading(threads),
#                         file="output/model_results/GLMMs/gtmn_den_glmm18.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- gtmn_n
models <- list(gtmn_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)

### Indian River-Vero Beach to Ft. Pierce Aquatic Preserve_Natural ----------------------------------------

irvb_n <- subset(oysterraw_den,
                 oysterraw_den$MA_plotlab==
                   "Indian River-Vero Beach to Ft. Pierce Aquatic Preserve_Natural")
irvb_n[, Density_m2 := as.integer(round(Density_m2))]
saveRDS(irvb_n, paste0('output/model_results/data/irvb_n_',
                       Sys.Date(), '.rds'))

irvb_den_glmm <- brm(formula=Density_m2 ~
                       RelYear+(0+RelYear | UniversalReefID),
                     data=irvb_n,
                     family=negbinomial, cores=ncores,
                     control= list(adapt_delta=0.995, max_treedepth=20),
                     iter=iter,
                     warmup=warmup, chains=nchains, init=0, thin=3, seed=5512,
                     backend="rstan", threads=threading(threads),
                     file="output/model_results/GLMMs/irvb_den_glmm9.rds")

# irvb_den_glmm <- update(irvb_den_glmm, 
#                         newdata = irvb_n,
#                         family=negbinomial, cores=ncores,
#                         control= list(adapt_delta=0.995, max_treedepth=20),
#                         iter=iter,
#                         warmup=warmup, chains=nchains, init=0, thin=3, seed=5512,
#                         backend="rstan", threads=threading(threads),
#                         file="output/model_results/GLMMs/irvb_den_glmm9.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- irvb_n
models <- list(irvb_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)

### Jensen Beach to Jupiter Inlet Aquatic Preserve_Natural ----------------------------------------

jbji_n <- subset(oysterraw_den,
                 oysterraw_den$MA_plotlab==
                   "Jensen Beach to Jupiter Inlet Aquatic Preserve_Natural")
jbji_n[, Density_m2 := as.integer(round(Density_m2))]
saveRDS(jbji_n, paste0('output/model_results/data/jbji_n_',
                       Sys.Date(), '.rds'))

jbji_den_glmm <- brm(formula=Density_m2 ~
                       RelYear+(0+RelYear | UniversalReefID),
                     data=jbji_n,
                     family=negbinomial, cores=ncores,
                     control= list(adapt_delta=0.995, max_treedepth=20),
                     iter=iter,
                     warmup=warmup, chains=nchains, init=0, thin=3, seed=5512,
                     backend="rstan", threads=threading(threads),
                     file="output/model_results/GLMMs/jbji_den_glmm9.rds")

# jbji_den_glmm <- update(irvb_den_glmm, 
#                         newdata = jbji_n,
#                         family=negbinomial, cores=ncores,
#                         control= list(adapt_delta=0.995, max_treedepth=20),
#                         iter=iter,
#                         warmup=warmup, chains=nchains, init=0, thin=3, seed=5512,
#                         backend="rstan", threads=threading(threads),
#                         file="output/model_results/GLMMs/jbji_den_glmm9.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- jbji_n
models <- list(jbji_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)

### Lemon Bay Aquatic Preserve_Natural ----------------------------------------

lb_n <- subset(oysterraw_den,
               oysterraw_den$MA_plotlab=="Lemon Bay Aquatic Preserve_Natural")
lb_n[, Density_m2 := as.integer(round(Density_m2))]
saveRDS(lb_n, paste0('output/model_results/data/lb_n_', Sys.Date(), '.rds'))

lb_den_glmm <- brm(formula=Density_m2 ~
                     RelYear+(1 | ReefIdentifier), data=lb_n,
                   family=zero_inflated_negbinomial, cores=2,
                   control= list(adapt_delta=0.995, max_treedepth=20),
                   iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
                   seed=4612, backend="rstan", threads=threading(threads),
                   file="output/model_results/GLMMs/lb_den_glmm6.rds")

# lb_den_glmm <- update(lb_den_glmm, 
#                       newdata = lb_n,
#                       family=zero_inflated_negbinomial, cores=2,
#                       control= list(adapt_delta=0.995, max_treedepth=20),
#                       iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                       seed=4612, backend="rstan", threads=threading(threads),
#                       file="output/model_results/GLMMs/lb_den_glmm6.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- lb_n
models <- list(lb_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)

### Pine Island Sound Aquatic Preserve_Natural ----------------------------------------

oysterraw_den[str_detect(MA_plotlab, "Pine Island Sound"), `:=`
              (MA_plotlab=ifelse(str_detect(ProgramLocationID, "Reference") |
                                   str_detect(ProgramLocationID, "Control"),
                                 "Pine Island Sound Aquatic Preserve_Natural",
                                 "Pine Island Sound Aquatic Preserve_Restored"),
                HabitatClassification=ifelse(str_detect(ProgramLocationID,
                                                        "Reference") |
                                               str_detect(ProgramLocationID,
                                                          "Control"),
                                             "Natural", "Restored"))]
pis_n <- subset(oysterraw_den,
                oysterraw_den$MA_plotlab==
                  "Pine Island Sound Aquatic Preserve_Natural")
pis_n[, `:=` (Density_m2=as.integer(round(Density_m2)),
              Treatment=ifelse(UniversalReefID==170711,
                               "Reference", "Control"))]
saveRDS(pis_n, paste0('output/model_results/data/pis_n_', Sys.Date(), '.rds'))

pis_den_glmm <- brm(formula=Density_m2 ~
                      RelYear+(0+RelYear | UniversalReefID),
                    data=pis_n, family=zero_inflated_negbinomial, cores=ncores,
                    control= list(adapt_delta=0.995, max_treedepth=20),
                    iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
                    seed=5243, backend="rstan", threads=threading(threads),
                    file="output/model_results/GLMMs/pis_den_glmm9.rds")

# pis_den_glmm <- update(pis_den_glmm, 
#                        newdata = pis_n,
#                        family=zero_inflated_negbinomial, cores=ncores,
#                        control= list(adapt_delta=0.995, max_treedepth=20),
#                        iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                        seed=5243, backend="rstan", threads=threading(threads),
#                        file="output/model_results/GLMMs/pis_den_glmm9.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- pis_n
models <- list(pis_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)


### Pine Island Sound Aquatic Preserve_Restored ----------------------------------------

pisr_n <- subset(oysterraw_den,
                 oysterraw_den$MA_plotlab==
                   "Pine Island Sound Aquatic Preserve_Restored")
pisr_n[, `:=` (Density_m2=as.integer(round(Density_m2)),
               Treatment=ifelse(UniversalReefID==170711,
                                "Reference", "Control"))]
saveRDS(pisr_n, paste0('output/model_results/data/pisr_n_', Sys.Date(), '.rds'))

pisr_den_glmm <- brm(formula=Density_m2 ~
                       RelYear+QuadSize_m2, data=pisr_n,
                     family=zero_inflated_negbinomial,
                     prior=set_prior("uniform(0,5)", class="b", lb=0, ub=5),
                     cores=ncores, control= list(adapt_delta=0.995, max_treedepth=20),
                     iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
                     seed=8441, backend="rstan", threads=threading(threads),
                     file="output/model_results/GLMMs/pisr_den_glmm12.rds")

# pisr_den_glmm <- update(pisr_den_glmm, 
#                         newdata = pisr_n,
#                         family=zero_inflated_negbinomial,
#                         prior=set_prior("uniform(0,5)", class="b", lb=0, ub=5),
#                         cores=ncores, control= list(adapt_delta=0.995, max_treedepth=20),
#                         iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                         seed=8441, backend="rstan", threads=threading(threads),
#                         file="output/model_results/GLMMs/pisr_den_glmm12.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- pisr_n
models <- list(pisr_den_glmm) 
modresults(data, models, "Density", meplotzoom=FALSE)

PI_R <- nrow(subset(oysterresults,
                    oysterresults$managed_area==
                      "Pine Island Sound Aquatic Preserve" &
                      oysterresults$indicator=="Density" &
                      oysterresults$habitat_class=="Restored"))

oysterresults$group[is.na(oysterresults$group)] <- NA

if(PI_R>0){
  oysterresults$group[oysterresults$managed_area==
                        "Pine Island Sound Aquatic Preserve" &
                        oysterresults$indicator=="Density" &
                        oysterresults$habitat_class=="Restored"] <-
    c(NA, NA, NA)
  
  oysterresults$term[oysterresults$managed_area==
                       "Pine Island Sound Aquatic Preserve" &
                       oysterresults$indicator=="Density" &
                       oysterresults$habitat_class=="Restored"] <-
    c("(Intercept)", "RelYear", "QuadSize_m2")
}
```



# Percent Live Analysis

Subsets data for that which is related to percent live. The data is further subset for each managed area. Appropriate GLMMs are called from file for each shell size class, or are created if they don't exist. Data and models are then sent to the modresults function to create figures and save data.

```{r PercentLive, eval=F, echo=T}
#Make a collapsed version of the oysterraw table for percent live
oysterraw_pct <- oysterraw[, c("ProgramID", "ProgramName", "ProgramLocationID",
                               "QuadIdentifier", "ReefIdentifier", "LiveDate",
                               "LiveDate_Qualifier", "SampleDate", "Year",
                               "Month", "ManagedAreaName", "Region",
                               "SurveyMethod", "PercentLiveMethod",
                               "HabitatClassification", "QuadSize_m2", "MADup",
                               "PercentLive_pct",
                               "Number_of_Oysters_Counted_Total_Count",
                               "Number_of_Oysters_Counted_Live_Count",
                               "Number_of_Oysters_Counted_Dead_Count",
                               "ObsIndex", "UniversalReefID",
                               "MA_plotlab", "Subtidal", "RelYear", "YearDiff")]
oysterraw_pct[!is.na(PercentLive_pct), PctIndex := ObsIndex]
oysterraw_pct[!is.na(Number_of_Oysters_Counted_Total_Count),
              NTotIndex := ObsIndex]
oysterraw_pct[!is.na(Number_of_Oysters_Counted_Live_Count),
              NLiveIndex := ObsIndex]
oysterraw_pct[!is.na(Number_of_Oysters_Counted_Dead_Count),
              NDeadIndex := ObsIndex]
oysterraw_pct[, ObsIndex := NULL]

oysterraw_pct <- unique(oysterraw_pct)
oysterraw_pct <- oysterraw_pct %>%
  dplyr::group_by(ProgramID, ProgramName, ProgramLocationID, QuadIdentifier,
                  ReefIdentifier, LiveDate, LiveDate_Qualifier, SampleDate,
                  Year, Month, ManagedAreaName, Region, SurveyMethod,
                  PercentLiveMethod, HabitatClassification, QuadSize_m2,
                  MADup, UniversalReefID, MA_plotlab, Subtidal,
                  RelYear) %>%
  tidyr::fill(PercentLive_pct, Number_of_Oysters_Counted_Total_Count,
              Number_of_Oysters_Counted_Live_Count,
              Number_of_Oysters_Counted_Dead_Count,
              PctIndex, NTotIndex, NLiveIndex, NDeadIndex) %>%
  tidyr::fill(PercentLive_pct, Number_of_Oysters_Counted_Total_Count,
              Number_of_Oysters_Counted_Live_Count,
              Number_of_Oysters_Counted_Dead_Count,
              PctIndex, NTotIndex, NLiveIndex, NDeadIndex, 
              .direction='up') %>%
  dplyr::distinct()

oysterraw_pct <- subset(oysterraw_pct, !is.na(oysterraw_pct$PercentLive_pct) |
                          !is.na(oysterraw_pct$Number_of_Oysters_Counted_Total_Count) |
                          !is.na(oysterraw_pct$Number_of_Oysters_Counted_Live_Count) |
                          !is.na(oysterraw_pct$Number_of_Oysters_Counted_Dead_Count) |
                          !is.na(oysterraw_pct$PctIndex) |
                          !is.na(oysterraw_pct$NTotIndex) |
                          !is.na(oysterraw_pct$NLiveIndex) |
                          !is.na(oysterraw_pct$NDeadIndex))
setDT(oysterraw_pct)

#Calculate PercentLive_pct values for some ProgramIDs where it is missing.
#Couldn't include at the start of the script because need to use the counts columns
#rather than the QuadSize_m2 column which is filled for the whole combined table.
oysterraw_pct[ProgramID==972 | ProgramID==4014 | ProgramID==4044,
              PercentLive_pct :=
                (Number_of_Oysters_Counted_Live_Count/
                   (Number_of_Oysters_Counted_Live_Count+
                      Number_of_Oysters_Counted_Dead_Count) * 100)]

#Filter NAs for PercentLive_pct (these are related to 1) programs that do
#counts to measure density, but do not estimate percent live and
#2) Programs that are listed as measuring percent live by a Point-intercept
#method, which cannot be calculated from counts.
oysterraw_pct <- oysterraw_pct[!is.na(PercentLive_pct), ]

#Add column of decimal versions of percent live values
oysterraw_pct[, PercentLive_dec := PercentLive_pct/100] 

#Summarize percent live values
pct_all_sum <- summarySE(oysterraw_pct, measurevar='PercentLive_pct',
                         groupvars=c('ManagedAreaName', 'Year', 'PercentLiveMethod'))


## Apalachicola Bay Aquatic Preserve_Natural ----------------------------------------

abap_p <- subset(oysterraw_pct,
                 oysterraw_pct$MA_plotlab==
                   "Apalachicola Bay Aquatic Preserve_Natural")
saveRDS(abap_p, paste0('output/model_results/data/abap_p_', Sys.Date(), '.rds'))

abap_p_binom <- data.table(ProgramID=character(), ProgramLocationID=character(),
                           QuadIdentifier=character(), Year=integer(),
                           ManagedAreaName=character(),
                           PercentLiveMethod=character(),
                           UniversalReefID=factor(), Region=character(),
                           MA_plotlab=character(), RelYear=integer(),
                           PercentLive_pct=numeric(), LiveObs=logical())
for(i in 1:nrow(abap_p)){
  dat_i <- abap_p[i, c("ProgramID", "ProgramLocationID", "QuadIdentifier",
                       "Year", "ManagedAreaName", "PercentLiveMethod",
                       "UniversalReefID", "Region", "MA_plotlab", "RelYear",
                       "PercentLive_pct")]
  dat_l <- purrr::map_dfr(seq_len(round(dat_i$PercentLive_pct[1], digits=0)),
                          ~dat_i[, LiveObs := 1])
  dat_nl <- purrr::map_dfr(seq_len((100-round(dat_i$PercentLive_pct[1],
                                              digits=0))),
                           ~dat_i[, LiveObs := 0])
  dat <- rbind(dat_l, dat_nl)
  abap_p_binom <- rbind(abap_p_binom, dat)
}
saveRDS(abap_p_binom,
        paste0('output/model_results/data/abap_p_binom_',
               Sys.Date(), '.rds'))

abap_pct_glmm <- brm(formula=LiveObs ~ RelYear+(1 | UniversalReefID),
                     data=abap_p_binom, family=bernoulli, cores=ncores,
                     control= list(adapt_delta=0.995,
                                   max_treedepth=20),
                     iter=iter, warmup=warmup, chains=nchains, init=0,
                     thin=3,
                     seed=4331, backend="rstan",
                     threads=threading(threads),
                     file="output/model_results/GLMMs/abap_pct_glmm3.rds")

# abap_pct_glmm <- update(abap_pct_glmm, 
#                         newdata = abap_p_binom,
#                         family=bernoulli, cores=ncores,
#                         control= list(adapt_delta=0.995,
#                                       max_treedepth=20),
#                         iter=iter, warmup=warmup, chains=nchains, init=0,thin=3,
#                         seed=4331, backend="rstan", threads=threading(threads),
#                         file="output/model_results/GLMMs/abap_pct_glmm3.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- abap_p
models <- list(abap_pct_glmm) 
modresults(data, models, "Percent live", meplotzoom=FALSE)

## Apalachicola National Estuarine Research Reserve_Natural ----------------------------------------

anerr_p <- subset(oysterraw_pct,
                  oysterraw_pct$MA_plotlab==
                    "Apalachicola National Estuarine Research Reserve_Natural")
saveRDS(anerr_p, paste0('output/model_results/data/anerr_p_', Sys.Date(), '.rds'))

anerr_p_binom <- data.table(ProgramID=character(), ProgramLocationID=character(),
                            QuadIdentifier=character(), Year=integer(),
                            ManagedAreaName=character(),
                            PercentLiveMethod=character(),
                            UniversalReefID=factor(), Region=character(),
                            MA_plotlab=character(), RelYear=integer(),
                            PercentLive_pct=numeric(), LiveObs=logical())
for(i in 1:nrow(anerr_p)){
  dat_i <- anerr_p[i, c("ProgramID", "ProgramLocationID", "QuadIdentifier",
                        "Year", "ManagedAreaName", "PercentLiveMethod",
                        "UniversalReefID", "Region", "MA_plotlab", "RelYear",
                        "PercentLive_pct")]
  dat_l <- purrr::map_dfr(seq_len(round(dat_i$PercentLive_pct[1], digits=0)),
                          ~dat_i[, LiveObs := 1])
  dat_nl <- purrr::map_dfr(seq_len((100-round(dat_i$PercentLive_pct[1],
                                              digits=0))),
                           ~dat_i[, LiveObs := 0])
  dat <- rbind(dat_l, dat_nl)
  anerr_p_binom <- rbind(anerr_p_binom, dat)
}
saveRDS(anerr_p_binom,
        paste0('output/model_results/data/anerr_p_binom_',
               Sys.Date(), '.rds'))

anerr_pct_glmm <- brm(formula=LiveObs ~ RelYear+(1 | UniversalReefID),
                      data=anerr_p_binom, family=bernoulli, cores=ncores,
                      control= list(adapt_delta=0.995,
                                    max_treedepth=20),
                      iter=iter, warmup=warmup, chains=nchains, init=0,
                      thin=3,
                      seed=4331, backend="rstan",
                      threads=threading(threads),
                      file="output/model_results/GLMMs/anerr_pct_glmm3.rds")

# anerr_pct_glmm <- update(anerr_pct_glmm, 
#                          newdata = anerr_p_binom,
#                          family=bernoulli, cores=ncores,
#                          control= list(adapt_delta=0.995,
#                                        max_treedepth=20),
#                          iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                          seed=4331, backend="rstan", threads=threading(threads),
#                          file="output/model_results/GLMMs/anerr_pct_glmm3.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- anerr_p
models <- list(anerr_pct_glmm) 
modresults(data, models, "Percent live", meplotzoom=FALSE)

## Guana River Marsh Aquatic Preserve_Natural ----------------------------------------

grm_p <- subset(oysterraw_pct,
                oysterraw_pct$MA_plotlab==
                  "Guana River Marsh Aquatic Preserve_Natural")
saveRDS(grm_p, paste0('output/model_results/data/grm_p_', Sys.Date(), '.rds'))

grm_p_binom <- data.table(ProgramID=character(), ProgramLocationID=character(),
                          QuadIdentifier=character(), Year=integer(),
                          ManagedAreaName=character(),
                          PercentLiveMethod=character(),
                          UniversalReefID=factor(), Region=character(),
                          MA_plotlab=character(), RelYear=integer(),
                          PercentLive_pct=numeric(), LiveObs=logical())
for(i in 1:nrow(grm_p)){
  dat_i <- grm_p[i, c("ProgramID", "ProgramLocationID", "QuadIdentifier",
                      "Year", "ManagedAreaName", "PercentLiveMethod",
                      "UniversalReefID", "Region", "MA_plotlab", "RelYear",
                      "PercentLive_pct")]
  dat_l <- purrr::map_dfr(seq_len(round(dat_i$PercentLive_pct[1], digits=0)),
                          ~dat_i[, LiveObs := 1])
  dat_nl <- purrr::map_dfr(seq_len((100-round(dat_i$PercentLive_pct[1],
                                              digits=0))),
                           ~dat_i[, LiveObs := 0])
  dat <- rbind(dat_l, dat_nl)
  grm_p_binom <- rbind(grm_p_binom, dat)
}
saveRDS(grm_p_binom, paste0('output/model_results/data/grm_p_binom_',
                            Sys.Date(), '.rds'))

grm_pct_glmm <- brm(formula=LiveObs ~ RelYear+(1 | UniversalReefID),
                    data=grm_p_binom, family=bernoulli, cores=ncores,
                    control= list(adapt_delta=0.995, max_treedepth=20),
                    iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
                    seed=4331, backend="rstan", threads=threading(threads),
                    file="output/model_results/GLMMs/grm_pct_glmm3.rds")

# grm_pct_glmm <- update(grm_pct_glmm, 
#                        newdata = grm_p_binom,
#                        family=bernoulli, cores=ncores,
#                        control= list(adapt_delta=0.995, max_treedepth=20),
#                        iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                        seed=4331, backend="rstan", threads=threading(threads),
#                        file="output/model_results/GLMMs/grm_pct_glmm3.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- grm_p
models <- list(grm_pct_glmm) 
modresults(data, models, "Percent live", meplotzoom=FALSE)

## Guana Tolomato Matanzas National Estuarine Research
## Reserve_Natural ----------------------------------------

gtm_p <- subset(oysterraw_pct,
                oysterraw_pct$MA_plotlab==
                  "Guana Tolomato Matanzas National Estuarine Research Reserve_Natural")
saveRDS(gtm_p, paste0('output/model_results/data/gtm_p_', Sys.Date(), '.rds'))

gtm_p_binom <- data.table(ProgramID=character(), ProgramLocationID=character(),
                          QuadIdentifier=character(), Year=integer(),
                          ManagedAreaName=character(),
                          PercentLiveMethod=character(),
                          UniversalReefID=factor(), Region=character(),
                          MA_plotlab=character(), RelYear=integer(),
                          PercentLive_pct=numeric(), LiveObs=logical())
for(i in 1:nrow(gtm_p)){
  dat_i <- gtm_p[i, c("ProgramID", "ProgramLocationID", "QuadIdentifier",
                      "Year", "ManagedAreaName", "PercentLiveMethod",
                      "UniversalReefID", "Region", "MA_plotlab", "RelYear",
                      "PercentLive_pct")]
  dat_l <- purrr::map_dfr(seq_len(round(dat_i$PercentLive_pct[1], digits=0)),
                          ~dat_i[, LiveObs := 1])
  dat_nl <- purrr::map_dfr(seq_len((100-round(dat_i$PercentLive_pct[1],
                                              digits=0))),
                           ~dat_i[, LiveObs := 0])
  dat <- rbind(dat_l, dat_nl)
  gtm_p_binom <- rbind(gtm_p_binom, dat)
}
saveRDS(gtm_p_binom,
        paste0('output/model_results/data/gtm_p_binom_',
               Sys.Date(), '.rds'))

gtm_pct_glmm <- brm(formula=LiveObs ~ RelYear+(1 | UniversalReefID),
                    data=gtm_p_binom, family=bernoulli, cores=ncores,
                    control= list(adapt_delta=0.995,
                                  max_treedepth=20),
                    iter=iter, warmup=warmup, chains=nchains, init=0,
                    thin=3,
                    seed=4331, backend="rstan",
                    threads=threading(threads),
                    file="output/model_results/GLMMs/gtm_pct_glmm3.rds")

# gtm_pct_glmm <- update(gtm_pct_glmm, 
#                        newdata = gtm_p_binom,
#                        family=bernoulli, cores=ncores,
#                        control= list(adapt_delta=0.995,
#                                      max_treedepth=20),
#                        iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                        seed=4331, backend="rstan", threads=threading(threads),
#                        file="output/model_results/GLMMs/gtm_pct_glmm3.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- gtm_p
models <- list(gtm_pct_glmm) 
modresults(data, models, "Percent live", meplotzoom=FALSE)


## Indian River-Vero Beach to Ft. Pierce Aquatic Preserve_Natural ----------------------------------------

irvb_p <- subset(oysterraw_pct,
                 oysterraw_pct$MA_plotlab==
                   "Indian River-Vero Beach to Ft. Pierce Aquatic Preserve_Natural")
saveRDS(irvb_p, paste0('output/model_results/data/irvb_p_', Sys.Date(), '.rds'))

irvb_p_binom <- data.table(ProgramID=character(), ProgramLocationID=character(),
                           QuadIdentifier=character(), Year=integer(),
                           ManagedAreaName=character(),
                           PercentLiveMethod=character(),
                           UniversalReefID=factor(), Region=character(),
                           MA_plotlab=character(), RelYear=integer(),
                           PercentLive_pct=numeric(), LiveObs=logical())
for(i in 1:nrow(irvb_p)){
  dat_i <- irvb_p[i, c("ProgramID", "ProgramLocationID", "QuadIdentifier",
                       "Year", "ManagedAreaName", "PercentLiveMethod",
                       "UniversalReefID", "Region", "MA_plotlab", "RelYear",
                       "PercentLive_pct")]
  dat_l <- purrr::map_dfr(seq_len(round(dat_i$PercentLive_pct[1], digits=0)),
                          ~dat_i[, LiveObs := 1])
  dat_nl <- purrr::map_dfr(seq_len((100-round(dat_i$PercentLive_pct[1],
                                              digits=0))),
                           ~dat_i[, LiveObs := 0])
  dat <- rbind(dat_l, dat_nl)
  irvb_p_binom <- rbind(irvb_p_binom, dat)
}
saveRDS(irvb_p_binom, paste0('output/model_results/data/irvb_p_binom_',
                             Sys.Date(), '.rds'))

irvb_pct_glmm <- brm(formula=LiveObs ~ RelYear+(1 | UniversalReefID),
                     data=irvb_p_binom, family=bernoulli, cores=ncores,
                     control= list(adapt_delta=0.995, max_treedepth=20),
                     iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
                     seed=4331, backend="rstan", threads=threading(threads),
                     file="output/model_results/GLMMs/irvb_pct_glmm3.rds")

# irvb_pct_glmm <- update(irvb_pct_glmm, 
#                         newdata = irvb_p_binom,
#                         family=bernoulli, cores=ncores,
#                         control= list(adapt_delta=0.995, max_treedepth=20),
#                         iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                         seed=4331, backend="rstan", threads=threading(threads),
#                         file="output/model_results/GLMMs/irvb_pct_glmm3.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- irvb_p
models <- list(irvb_pct_glmm) 
modresults(data, models, "Percent live", meplotzoom=FALSE)


## Jensen Beach to Jupiter Inlet Aquatic Preserve_Natural ----------------------------------------

jbji_p <- subset(oysterraw_pct,
                 oysterraw_pct$MA_plotlab==
                   "Jensen Beach to Jupiter Inlet Aquatic Preserve_Natural")
saveRDS(jbji_p, paste0('output/model_results/data/jbji_p_', Sys.Date(), '.rds'))

jbji_p_binom <- data.table(ProgramID=character(), ProgramLocationID=character(),
                           QuadIdentifier=character(), Year=integer(),
                           ManagedAreaName=character(),
                           PercentLiveMethod=character(),
                           UniversalReefID=factor(), Region=character(),
                           MA_plotlab=character(), RelYear=integer(),
                           PercentLive_pct=numeric(), LiveObs=logical())
for(i in 1:nrow(jbji_p)){
  dat_i <- jbji_p[i, c("ProgramID", "ProgramLocationID", "QuadIdentifier",
                       "Year", "ManagedAreaName", "PercentLiveMethod",
                       "UniversalReefID", "Region", "MA_plotlab", "RelYear",
                       "PercentLive_pct")]
  dat_l <- purrr::map_dfr(seq_len(round(dat_i$PercentLive_pct[1], digits=0)),
                          ~dat_i[, LiveObs := 1])
  dat_nl <- purrr::map_dfr(seq_len((100-round(dat_i$PercentLive_pct[1],
                                              digits=0))),
                           ~dat_i[, LiveObs := 0])
  dat <- rbind(dat_l, dat_nl)
  jbji_p_binom <- rbind(jbji_p_binom, dat)
}
saveRDS(jbji_p_binom, paste0('output/model_results/data/jbji_p_binom_',
                             Sys.Date(), '.rds'))

jbji_pct_glmm <- brm(formula=LiveObs ~ RelYear+(1 | UniversalReefID),
                     data=jbji_p_binom, family=bernoulli, cores=ncores,
                     control= list(adapt_delta=0.995, max_treedepth=20),
                     iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
                     seed=4331, backend="rstan", threads=threading(threads),
                     file="output/model_results/GLMMs/jbji_pct_glmm3.rds")

# jbji_pct_glmm <- update(jbji_pct_glmm, 
#                         newdata = jbji_p_binom,
#                         family=bernoulli, cores=ncores,
#                         control= list(adapt_delta=0.995, max_treedepth=20),
#                         iter=iter, warmup=warmup, chains=nchains, init=0, thin=3,
#                         seed=4331, backend="rstan", threads=threading(threads),
#                         file="output/model_results/GLMMs/jbji_pct_glmm3.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- jbji_p
models <- list(jbji_pct_glmm) 
modresults(data, models, "Percent live", meplotzoom=FALSE)

## Lemon Bay Aquatic Preserve_Natural ----------------------------------------

lb_p <- subset(oysterraw_pct,
               oysterraw_pct$MA_plotlab=="Lemon Bay Aquatic Preserve_Natural")
lb_p[, PercentLive_dec := PercentLive_pct/100]
#PercentLiveMethod=="Percent" for Lemon Bay program(s) with sufficient data,
#so cannot be modeled as binomial
saveRDS(lb_p, paste0('output/model_results/data/lb_p_', Sys.Date(), '.rds'))

lb_pct_glmm <- brm(formula=PercentLive_dec ~
                     RelYear+(0+RelYear | ReefIdentifier),
                   data=subset(lb_p, lb_p$PercentLive_dec > 0 & lb_p$PercentLive_dec < 1),family=Beta,
                   cores=ncores, control= list(adapt_delta=0.995, max_treedepth=20),
                   iter=iter, warmup=warmup, chains=nchains, init=0, thin=3, seed=8465,
                   backend="rstan", threads=threading(threads),
                   file="output/model_results/GLMMs/lb_pct_glmm6.rds")

# lb_pct_glmm <- update(lb_pct_glmm, 
#                       newdata = subset(lb_p, lb_p$PercentLive_dec > 0),
#                       family=Beta,
#                       cores=ncores, control= list(adapt_delta=0.995, max_treedepth=20),
#                       iter=iter, warmup=warmup, chains=nchains, init=0, thin=3, seed=8465,
#                       backend="rstan", threads=threading(threads),
#                       file="output/model_results/GLMMs/lb_pct_glmm6.rds")

# Create model results tables and save diagnostic plots and marginal effects plots
data <- lb_p
models <- list(lb_pct_glmm) 
modresults(data, models, "Percent live", meplotzoom=FALSE)
```



# Save & Export Results

The compiled model results variable is saved to a csv and rds file. The model results are evaluated to see if any models need to be reconsidered based on the rhat convergence being over 1.05. rhat values are written to file.

```{r SaveResults, eval=F, echo=T}
fwrite(oysterresults, paste0("output/GLMM_AllDates_ModelResults.csv"), sep=",")
saveRDS(oysterresults, paste0("output/GLMM_AllDates_ModelResults.rds"))

#Get Rhat values for all models to check which ones may need to be reparameterized
model_list <- unique(oysterresults$filename)
rhats_all <- data.table(filename=character(),
                        term=character(),
                        rhat=numeric())
rhats_sum <- data.table(filename=character(),
                        rhat=numeric())

for(mod in model_list){
  mod_i <- readRDS(mod)
  allrhat_i <- rhat(mod_i)
  sumrhat_i <- c(summary(mod_i)$fixed$Rhat, summary(mod_i)$spec_pars$Rhat)
  allrhat_model_i <- data.table(filename=mod,
                                term=names(allrhat_i),
                                rhat=allrhat_i)
  sumrhat_model_i <- data.table(filename=mod,
                                rhat=sumrhat_i)
  rhats_all <- rbind(rhats_all, allrhat_model_i)
  rhats_sum <- rbind(rhats_sum, sumrhat_model_i)
}

rhats_all[, rhat_r := round(rhat, 2)]
rhats_sum[, rhat_r := round(rhat, 2)]

saveRDS(rhats_all, paste0("output/rhats_all_", Sys.Date(), ".rds"))
saveRDS(rhats_sum, paste0("output/rhats_sum_", Sys.Date(), ".rds"))

models_to_check_allrhat <- unique(rhats_all[rhat_r > 1.05, filename])
models_to_check_sumrhat <- unique(rhats_sum[rhat_r > 1.05, filename])

# Zip all figures
for(p in c("Density", "Percent_Live", "Shell_Height")){
  out_dir <- paste0("output/", p)
  fig_list <- list.files(paste0(out_dir, "/Figures"), pattern=".png", full=FALSE)
  filename <- paste0("Oyster", gsub("_", "", p), "Figures")
  setwd(paste0(out_dir, "/Figures"))
  zip(filename, files=fig_list)
  setwd(wd)
}
```

```{r, functions to plot oysters, eval=T, echo=F}
# Read in oyster results file
oyster_stats <- fread("output/Oyster_All_GLMM_Stats.txt", sep='|')
# Function to add trend text
trendText <- function(modelEstimate, lowConfidence, upConfidence){
  increasing <- modelEstimate > 0
  trendPresent <- ifelse(lowConfidence < 0 & upConfidence < 0, TRUE, 
                         ifelse(lowConfidence > 0 & upConfidence > 0, TRUE, FALSE))
  trendStatus <- "No significant change"
  if(trendPresent){
    trendDirection <- ifelse(increasing, "increasing", "decreasing")
    trendStatus <- paste0("Significantly ", trendDirection, " trend")
  }
  return(trendStatus)
}
# Apply function, add credible interval
oyster_stats <- oyster_stats %>% rowwise() %>%
  mutate(
    "Trend Status" = ifelse(!is.na(ModelEstimate), trendText(ModelEstimate, LowerConfidence, UpperConfidence), NA),
    "Credible Interval" = paste0(round(LowerConfidence, 2), " to ", round(UpperConfidence, 2))
  ) %>%
  ungroup() %>% as.data.table()

# Oyster plot locations
oy_figs <- list(
  "Density" = list.files("output/Density/Figures", pattern = ".png", full.names = T),
  "Percent Live" = list.files("output/Percent_Live/Figures", pattern = ".png", full.names = T),
  "Shell Height" = list.files("output/Shell_Height/Figures", pattern = ".png", full.names = T)
)

# Dataframe to determine which figures are included
oyster_includes <- oyster_stats %>% 
  group_by(ManagedAreaName, ParameterName, SufficientData, HabitatType, Intercept) %>%
  filter(SufficientData, !is.na(Intercept)) %>%
  summarise(.groups = "keep") %>% as.data.table()

# Function to locate oyster figures
oy_file_loc <- function(ma_abrev, p, type){
  if(p=="Density"){
    pattern <- paste0("_GLMM_", ma_abrev,"_",type,"raw.png")
  } else if(p=="Percent Live"){
    pattern <- paste0("_GLMM_", ma_abrev,"_raw.png")
  } else if(p=="Shell Height"){
    pattern <- paste0("_GLMM_", ma_abrev,".png")
  }
  return(str_subset(oy_figs[[p]], pattern))
}

# Function to display oyster results tables
oyster_tables <- function(ma, p, type){
  subset <- oyster_stats[ManagedAreaName==ma & ParameterName==p & HabitatType==type,]
  ResultTable <- subset %>% 
    select(ShellType, HabitatType, "Trend Status", ModelEstimate, StandardError, 
           "Credible Interval") %>%
    rename("Shell Type" = "ShellType",
           "Habitat Type" = "HabitatType",
           "Estimate" = "ModelEstimate",
           "Standard Error" = "StandardError")
  
  result_table <- kable(ResultTable, format = "latex",
                        caption = paste0("Model results for Oyster ", p, " - ", type),
                        row.names = FALSE, digits = 2,
                        booktabs = T, linesep = "", escape = F, longtable = F) %>%
    row_spec(row = 0, italic = TRUE) %>%
    kable_styling(latex_options = c("scale_down", "HOLD_position"))
  
  print(result_table)
}

# Function to allow dynamic plot sizes
subchunkify <- function(g, fig_height=9, fig_width=10, fig_cap) {
  g_deparsed <- paste0(deparse(
    function() {g}
  ), collapse = '')

  sub_chunk <- paste0("
  \n`","``{r sub_chunk_", floor(runif(1) * 10000), ", fig.height=",
   fig_height, ", fig.width=", fig_width, ", echo=FALSE, results='asis'}",
  "\n(", 
    g_deparsed
    , ")()",
  "\n`","``
  ")

  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}
```

```{r, Oyster figures, eval=T, echo=F, results='asis'}
## Begin report display
cat("\\newpage")
cat("  \n")
cat("# Oyster Figures")
cat("  \n")

for(p in unique(oyster_includes$ParameterName)){
  # parameter subset
  p_subset <- oyster_includes[ParameterName==p, ]
  cat("  \n")
  cat(glue("# {p}"))
  cat("  \n")
  # Find managed areas with figures for that parameter
  for(ma in unique(p_subset$ManagedAreaName)){
    ma_subset <- p_subset[ManagedAreaName==ma, ]
    ma_abrev <- MA_All[ManagedAreaName==ma, Abbreviation]
    cat(glue("## {ma}"))
    hab_types <- unique(ma_subset$HabitatType)
    for(type in hab_types){
      type_subset <- ma_subset[HabitatType==type, ]
      if(nrow(type_subset)>0){
        cat("  \n")
        cat(glue("### {type}"))
        cat("  \n")
        plot_loc <- oy_file_loc(ma_abrev, p, type)
        fig_caption <- paste0("Figure for Oyster ", p, " in ", ma)
        subchunkify(cat("![", fig_caption, "](", plot_loc,")"))
        cat("  \n")
        oyster_tables(ma, p, type)
        cat("  \n")
      }
    }
  }
}

```